---
title: Graph Gallery
---

ðŸ‘‹ **Bizard** is a comprehensive repository of advanced visualization codes tailored for biomedical research. It currently includes approximately 750 graphics across more than 65 chart types. Below is the gallery for all graphics. 

Each graph is a row in the table. You can click on the graph to zoom in for a preview. Clicking on the blue title of a graph will take you to the corresponding graphic tutorial page. The table's Search box provides graph search function.

```{r}
#| echo: false
#| message: false
#| warning: false

library(reactable)
library(jsonlite)
library(dplyr)
library(crosstalk)
library(htmltools)

data <- read.csv("files/gallery_data.csv")
```

## ðð€ð’ðˆð‚ð’

### Distribution Gallery

```{r}
#| echo: false
data_Distribution <- data[data$Level2=="Distribution",]

tbl <- reactable(
  data_Distribution,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Correlation Gallery

```{r}
#| echo: false
data_Correlation <- data[data$Level2=="Correlation",]

tbl <- reactable(
  data_Correlation,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Ranking Gallery

```{r}
#| echo: false
data_Ranking <- data[data$Level2=="Ranking",]

tbl <- reactable(
  data_Ranking,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Composition/Part Of The Whole Gallery

```{r}
#| echo: false
data_Ranking <- data[data$Level2=="Composition",]

tbl <- reactable(
  data_Ranking,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Data Over Time/Evolution Gallery

```{r}
#| echo: false
data_Ranking <- data[data$Level2=="Evolution",]

tbl <- reactable(
  data_Ranking,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Proportion/Flow Gallery

```{r}
#| echo: false
data_Ranking <- data[data$Level2=="Proportion",]

tbl <- reactable(
  data_Ranking,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Animation Gallery

```{r}
#| echo: false
data_Ranking <- data[data$Level2=="Animation",]

tbl <- reactable(
  data_Ranking,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

## ðŽðŒðˆð‚ð’

```{r}
#| echo: false
data_OMICS <- data[data$Level1=="OMICS",]

tbl <- reactable(
  data_OMICS,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```


## ð‚ð‹ðˆððˆð‚ð’

```{r}
#| echo: false
data_OMICS <- data[data$Level1=="CLINICS",]

tbl <- reactable(
  data_OMICS,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

## ð‡ðˆðð‹ðŽð“

### BASICS

```{r}
#| echo: false
data_HIPLOT_BASICS <- data[data$Level1=="HIPLOT" & data$Level2=="BASICS",]

tbl <- reactable(
  data_HIPLOT_BASICS,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### OMICS

```{r}
#| echo: false
data_HIPLOT_OMICS <- data[data$Level1=="HIPLOT" & data$Level2=="OMICS",]

tbl <- reactable(
  data_HIPLOT_OMICS,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### CLINICS

```{r}
#| echo: false
data_HIPLOT_CLINICS <- data[data$Level1=="HIPLOT" & data$Level2=="CLINICS",]

tbl <- reactable(
  data_HIPLOT_CLINICS,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### MAP

```{r}
#| echo: false
data_HIPLOT_MAP <- data[data$Level1=="HIPLOT" & data$Level2=="MAP",]

tbl <- reactable(
  data_HIPLOT_MAP,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```






```{js, echo=FALSE}

function renderGraph(cellInfo) {
  const url = cellInfo.row['Tutorial_url']
  const imageSrc = cellInfo.row['Image_url']
  const altText = cellInfo.value
  const description = cellInfo.row['Description']
  const poster = `<img src="${imageSrc}" class="movie-poster" alt="${altText}" onclick="showModal(this)">`

  const title = `<a href="${url}" target="_blank">${cellInfo.value}</a>`

  const details = `<div class="movie-info-details">${description}</div>`
  const text = `<div class="movie-info-text">${title}${details}</div>`
  return `<div class="movie-info">${poster}${text}</div>`
}

function showModal(image) {
  var modal = document.getElementById("modal");
  var modalImage = document.getElementById("modal-image");
  modal.style.display = "block";
  modalImage.src = image.src;
}

function hideModal() {
  var modal = document.getElementById("modal");
  modal.style.display = "none";
}
```

```{css, echo=FALSE}

/* Font from https://fontsarena.com/hanken-grotesk-by-hanken-design-co/ */
@font-face {
  font-family: 'Hanken Grotesk';
  font-style: normal;
  font-weight: 400;
  src: url("fonts/HKGrotesk-Regular.woff2") format("woff2"),
       url("fonts/HKGrotesk-Regular.woff") format("woff");
}

@font-face {
  font-family: 'Hanken Grotesk';
  font-style: normal;
  font-weight: 600;
  src: url("fonts/HKGrotesk-SemiBold.woff2") format("woff2"),
       url("fonts/HKGrotesk-SemiBold.woff") format("woff");
}

@font-face {
  font-family: 'Hanken Grotesk';
  font-style: normal;
  font-weight: 700;
  src: url("fonts/HKGrotesk-Bold.woff2") format("woff2"),
       url("fonts/HKGrotesk-Bold.woff") format("woff");
}

.movies {
  font-family: 'Hanken Grotesk', Helvetica, Arial, sans-serif;
}

.movies h2 {
  font-weight: 600;
}

.movies a {
  color: #007899;
  text-decoration: none;
}

.movies a:hover,
.movies a:focus {
  text-decoration: underline;
  text-decoration-thickness: max(1px, 0.0625rem);
}

.movies-tbl {
  margin-top: 1rem;
  font-size: 1rem;
}

.header {
  color: hsl(0, 0%, 45%);
  font-weight: 700;
  font-size: 0.8125rem;
  letter-spacing: 0.4px;
  text-transform: uppercase;
}

.header:hover[aria-sort],
.header[aria-sort='ascending'],
.header[aria-sort='descending'] {
  color: hsl(0, 0%, 5%);
}

.movie-info {
  display: flex;
  align-items: center;
}

.movie-info-text {
  margin-left: 0.75rem;
  font-weight: 600;
  overflow: hidden;
  text-overflow: ellipsis;
}

.movie-info-details {
  margin-top: 0.125rem;
  font-size: 0.875rem;
  font-weight: 400;
  color: hsl(0, 0%, 40%);
  overflow: hidden;
  text-overflow: ellipsis;
}

.movie-poster {
  width: 100px;
  height: 100px;
  box-shadow: 0 0 0 1px hsl(0, 0%, 95%);
  cursor: zoom-in;
}

.movie-runtime {
  display: inline-block;
}

.movie-rating {
  margin-right: 0.25rem;
  padding: 0 0.25rem;
  border: 1px solid hsl(0, 0%, 75%);
  border-radius: 2px;
}

.user-score {
  font-weight: 600;
}

.filters {
  display: flex;
  flex-wrap: wrap;
  margin-top: 1rem;
  margin-left: -32px;
}

.filter-input {
  margin-top: 0.5rem;
  margin-left: 32px;
  flex: 1;
  min-width: 250px;
}

.filter-input label {
  color: hsl(0, 0%, 45%);
  font-weight: 700;
  font-size: 0.8125rem;
  letter-spacing: 0.4px;
  text-transform: uppercase;
}

.filter-input select,
.filter-input input[type="search"] {
  padding: 0 0.375rem;
  height: 2rem;
}

.filter-input input[type="search"] {
  /* Revert Bootstrap 5's Reboot styles, which change native search input styling */
  -webkit-appearance: searchfield;
  outline-offset: revert;
  border-color: revert;
}


.modal {
  display: none;
  position: fixed;
  z-index: 9999;
  top: 0;
  left: 0;
  width: 100%;
  height: 100%;
  background-color: rgba(0, 0, 0, 0.8);
  cursor: zoom-out;
}

.modal-image {
  display: block;
  max-width: 90%;
  max-height: 90%;
  margin: auto;
  margin-top: 5%;
}
```
