---
title: "Barcode Plot"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Barcode Plot` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/barcode-plot?lang=en>
:::

Barcode Plot is Suitable for displaying the distribution of large amounts of data.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The case data represents the sales revenue of a certain product in 500 stores in three regions.

```{r load data, message=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/barcode-plot/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1Barcode-plot}
#| label: fig-1Barcode-plot
#| fig-cap: "Barcode Plot"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 8
#| warning: false

# Barcode Plot
p <- ggplot(data, aes(x = sales, y = region)) +
  geom_tile(width = 0.01, height = 0.9, fill = "#606fcc") + # Control the width and height of the Barcode
  theme_bw() +
  labs(title = "Sales report", x = "Sales", y = "Region") +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

Through the barcode plot, we can observe that the number of stores with sales revenue around 50 is relatively high in Guangdong and Fujian regions. Additionally, the sales revenue among stores in Guangdong shows less variation, indicating a more concentrated distribution.

::: callout-tip
**Special Parameters: **

- **width**: Width of the bars
- **height**: Height of the bars
- **fill**: Color of the bars
:::

