---
title: "Barplot Gradient"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Barplot Gradient` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/barplot-gradient?lang=en>
:::

It is similar to the bubble chart, but on the basis of the histogram, a color gradient rectangle is used to simultaneously display the visualization of two variables.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `stringr`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("stringr", quietly = TRUE)) {
  install.packages("stringr")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(stringr)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The first column is Go Term (Go language code), the second column is the number of genes, and the third column is pvalue.

```{r load data, message=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/barplot-gradient/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data[, 1] <- str_to_sentence(str_remove(data[, 1], pattern = "\\w+:\\d+\\W"))
topnum <- 7
data <- data[1:topnum, ]
data[, 1] <- factor(data[, 1], level = rev(unique(data[, 1])))

# View data
head(data)
```

## Visualization

```{r fig-1Barplot-gradient}
#| label: fig-1Barplot-gradient
#| fig-cap: "Barplot Gradient"
#| out.width: "95%"
#| fig-height: 3
#| fig-width: 6
#| warning: false

# Barplot Gradient
p <- ggplot(data, aes(x = Term, y = Count, fill = -log10(PValue))) +
  geom_bar(stat = "identity") +
  ggtitle("GO BarPlot") +
  scale_fill_continuous(low = "#00438E", high = "#E43535") +
  scale_x_discrete(labels = function(x) {str_wrap(x, width = 65)}) +
  labs(fill = "-log10 (PValue)", y = "Term", x = "Count") +
  coord_flip() +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

As shown in the figure, blue is a low pvalue color, and red is a high pvalue color. As the pvalue increases, the color changes from blue to red. The abscissa indicates the number of genes.



