---
title: "Beanplot"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Beanplot` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/beanplot?lang=en>
:::

The beanplot is a method of visualizing the distribution characteristics.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplotify`; `beanplot`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}
if (!requireNamespace("beanplot", quietly = TRUE)) {
  install.packages("beanplot")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplotify)
library(beanplot)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data is data set (data on treatment outcomes of different treatment regimens).

```{r load data, message=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/beanplot/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
GroupOrder <- as.numeric(factor(data[, 2], levels = unique(data[, 2])))
data[, 2] <- paste0(data[,2], " ", as.numeric(factor(data[, 3])))
data <- cbind(data, GroupOrder)

# View data
head(data)
```

## Visualization

```{r fig-1Beanplot}
#| label: fig-1Beanplot
#| fig-cap: "Beanplot"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 7
#| warning: false

# Beanplot
p <- as.ggplot(function() {
  beanplot(Y ~ reorder(X, GroupOrder, mean), data = data, ll = 0.04,
           main = "Bean Plot", ylab = "Y", xlab = "X", side = "both",
           border = NA, horizontal = F, 
           col = list(c("#2b70c4", "#2b70c4"),c("#e9c216", "#e9c216")),
           beanlines = "mean", overallline = "mean", kernel = "gaussian")
  
  legend("bottomright", fill = c("#2b70c4", "#e9c216"),
         legend = levels(factor(data[, 3])))
})

p
```

