---
title: "Corrplot Big Data"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Corrplot Big Data` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/big-corrplot?lang=en>
:::

The correlation heat map is a graph that analyzes the correlation between two or more variables.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ComplexHeatmap`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ComplexHeatmap", quietly = TRUE)) {
  BiocManager::install("ComplexHeatmap")
}

# Load packages
library(data.table)
library(jsonlite)
library(ComplexHeatmap)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data are the gene names and the expression of each sample.

```{r load data, message=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/big-corrplot/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data <- data[!is.na(data[, 1]), ]
idx <- duplicated(data[, 1])
data[idx, 1] <- paste0(data[idx, 1], "--dup-", cumsum(idx)[idx])
rownames(data) <- data[, 1]
data <- data[, -1]
str2num_df <- function(x) {
  x[] <- lapply(x, function(l) as.numeric(l))
  x
}
tmp <- t(str2num_df(data))
corr <- round(cor(tmp, use = "na.or.complete", method = "pearson"), 3)

# View data
head(corr[,1:5])
```

## Visualization

```{r fig-1Big-corrplot}
#| label: fig-1Big-corrplot
#| fig-cap: "Corrplot Big Data"
#| out.width: "95%"
#| fig-height: 9
#| fig-width: 9
#| warning: false

# Corrplot Big Data
p <- ComplexHeatmap::Heatmap(
  corr, col = colorRampPalette(c("#4477AA","#FFFFFF","#BB4444"))(50),
  clustering_distance_rows = "euclidean",
  clustering_method_rows = "ward.D2",
  clustering_distance_columns = "euclidean",
  clustering_method_columns = "ward.D2",
  show_column_dend = FALSE, show_row_dend = FALSE,
  column_names_gp = gpar(fontsize = 8),
  row_names_gp = gpar(fontsize = 8)
)

p
```

Red indicates positive correlation between two genes, blue indicates negative correlation between two genes, and the number in each cell indicates correlation coefficient.


