---
title: "Bubble"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Bubble` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/bubble?lang=en>
:::

The bubble chart is a statistical chart that shows the third variable by the size of the bubble on the basis of the scatter chart, so that the three variables can be compared and analyzed simultaneously.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `stringr`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("stringr", quietly = TRUE)) {
  install.packages("stringr")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(stringr)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data are GO Term,Gene Ridio, Gene count and P-value.

```{r load data, message=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/bubble/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data[, 1] <- str_to_sentence(str_remove(data[, 1], pattern = "\\w+:\\d+\\W"))
topnum <- 7
data <- data[1:topnum, ]
data[, 1] <- factor(data[, 1], level = rev(unique(data[, 1])))

# View data
head(data)
```

## Visualization

```{r fig-1Bubble}
#| label: fig-1Bubble
#| fig-cap: "Bubble"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 6
#| warning: false

# Bubble
p <- ggplot(data, aes(Ratio, Term)) +
  geom_point(aes(size = Count, colour = -log10(PValue))) +
  scale_colour_gradient(low = "#00438E", high = "#E43535") +
  labs(colour = "-log10 (PValue)", size = "Count", x = "Ratio", y = "Term", 
       title = "Bubble Plot") +
  scale_x_continuous(limits = c(0, max(data$Ratio) * 1.2)) +
  guides(color = guide_colorbar(order = 1), size = guide_legend(order = 2)) +
  scale_y_discrete(labels = function(x) {str_wrap(x, width = 65)}) +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

The x-axis represents Gene Ridio, and the y-axis is GO Term; The size of the dot represents the number of genes, and the color of the dot represents the high or low P value.




