---
title: "Chi-square-fisher Test"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Chi-square-fisher Test` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/chi-square-fisher?lang=en>
:::

Chi-square and Fisher test can be used to test the frequency difference of categorical variables. The tool will automatically select the statistical method of Chi-square and Fisher exact test.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `visdat`; `aplot`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("visdat", quietly = TRUE)) {
  install.packages("visdat")
}
if (!requireNamespace("aplot", quietly = TRUE)) {
  install.packages("aplot")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(visdat)
library(aplot)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The data table supports two formats: contingency table (example 1) and single-row record table (example 2)

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/chi-square-fisher/data.json")$exampleData[[1]]$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
rownames(data) <- data[,1]
data <- data[,-1]
cb <- combn(nrow(data), 2)
final <- data.frame()
for (i in 1:ncol(cb)) {
  tmp <- data[cb[,i],]
  groups <- paste0(rownames(data)[cb[,i]], collapse = " | ")
  
  res <- tryCatch({
    chisq.test(tmp)
    }, warning = function(w) {
      tryCatch({fisher.test(tmp)}, error = function(e) {
        return(fisher.test(tmp, simulate.p.value = TRUE))
        })
  })
  val_percent <- apply(tmp, 1, function(x) {
    sprintf("%s (%s%%)", x, round(x / sum(x), 2) * 100)
  })
  val_percent1 <- paste0(colnames(tmp), ":", val_percent[,1])
  val_percent1 <- paste0(val_percent1, collapse = " | ")
  val_percent2 <- paste0(colnames(tmp), ":", val_percent[,2])
  val_percent2 <- paste0(val_percent2, collapse = " | ")
  tmp <- data.frame(
    groups = groups,
    val_percent_left = val_percent1,
    val_percent_right = val_percent2,
    statistic = ifelse(is.null(res$statistic), NA,
      as.numeric(res$statistic)),
    pvalue = as.numeric(res$p.value),
    method = res$method
  )
  final <- rbind(final, tmp)
}
final <- as.data.frame(final)
final$pvalue < as.numeric(final$pvalue)
final$statistic < as.numeric(final$statistic)

# View data
head(final)
```

## Visualization

```{r fig-1Chi-square-fisher}
#| label: fig-1Chi-square-fisher
#| fig-cap: "Chi-square-fisher Test"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 7
#| warning: false
#| message: false

# Chi-square-fisher Test
p1 <- vis_value(final["statistic"]) + 
  scale_fill_gradientn(colours = c("#3362ab","#87b7d7","#e8e0db","#eea07d","#ad1c2e"))

p2 <- vis_expect(final["pvalue"], ~.x < 0.05) +
  scale_fill_manual(values = c("#1c438a","#e7120c"))

p <- p1+p2
p
```

