---
title: "Chord Plot"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Chord Plot` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/chord?lang=en>
:::

The complex interaction is visualized in the form of chord graph.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `circlize`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("circlize", quietly = TRUE)) {
  install.packages("circlize")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(data.table)
library(jsonlite)
library(circlize)
library(ggplotify)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

Data frame or matrix of interaction of genes with pathways or gene ontologys.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/chord/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
row.names(data) <- data[, 1]
data <- data[, -1]
data <- as.matrix(data)

# View data
head(data)
```

## Visualization

```{r fig-1Chi-square-fisher}
#| label: fig-1Chord
#| fig-cap: "Chord Plot"
#| out.width: "95%"
#| warning: false
#| message: false
#| fig-height: 6
#| fig-width: 6

# Chord Plot
Palette <- c("#E64B35FF","#4DBBD5FF","#00A087FF","#3C5488FF","#F39B7FFF",
             "#8491B4FF","#91D1C2FF","#DC0000FF","#7E6148FF","#B09C85FF")
grid.col <- c(Palette, Palette, Palette[1:5])
p <- as.ggplot(function() {
  chordDiagram(
    data, grid.col = grid.col, grid.border = NULL, transparency = 0.5,
    row.col = NULL, column.col = NULL,  order = NULL,
    directional = 0, # 1, -1, 0, 2
    direction.type = "diffHeight", # diffHeight and arrows
    diffHeight = convert_height(2, "mm"), reduce = 1e-5, xmax = NULL, 
    self.link = 2, symmetric = FALSE, keep.diagonal = FALSE, 
    preAllocateTracks = NULL,
    annotationTrack = c("name", "grid", "axis"),
    annotationTrackHeight = convert_height(c(3, 3), "mm"),
    link.border = NA, link.lwd = par("lwd"), link.lty = par("lty"), 
    link.sort = FALSE, link.decreasing = TRUE, link.largest.ontop = FALSE,
    link.visible = T, link.rank = NULL, link.overlap = FALSE,
    scale = F, group = NULL, big.gap = 10, small.gap = 1
    )
  })

p
```




