---
title: "Circle Packing"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Circle Packing` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/circle-packing?lang=en>
:::

Circle packing is a visualization method used to display the differences in quantity among different categories.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `packcircles`; `ggplot2`; `viridis`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("packcircles", quietly = TRUE)) {
  install.packages("packcircles")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("viridis", quietly = TRUE)) {
  install.packages("viridis")
}

# Load packages
library(data.table)
library(jsonlite)
library(packcircles)
library(ggplot2)
library(viridis)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/circle-packing/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
packing <- circleProgressiveLayout(data[["v"]], sizetype = "area")
data <- cbind(data, packing)
dat_gg <- circleLayoutVertices(packing, npoints = 50)
colors <- c("#E57164","#F8ECA7","#9389C1","#3F9C78","#769F8D","#E5F9A9","#7CE9A4",
            "#CE9FCA","#78F197","#8BB085","#D88880","#A6E4C3","#F7F6B1","#C5E69A",
            "#F45FDE","#5CF371","#9259CF","#2B6D9B","#F3C096","#EEADBE")
dat_gg$value <- rep(colors, each = 51)

# View data
head(data)
```

## Visualization

```{r fig-1Circle-packing}
#| label: fig-1Circle-packing
#| fig-cap: "Circle Packing"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 8
#| warning: false
#| message: false

# Circle Packing
p <- ggplot() +
  geom_polygon(data = dat_gg, aes(x, y, group = id, fill = value), colour = "black", alpha = 0.4) +
  scale_fill_manual(values = magma(nrow(data))) +
  theme_void() +
  theme(legend.position = "none") +
  coord_equal() +
  scale_size_continuous(range = c(2.3, 4.5)) +
  geom_text(data = data, aes(x, y, size = v, label = g), vjust = 0) +
  geom_text(data = data, aes(x, y, label = v, size = v), vjust = 1.2)

p
```



