---
title: "Circular Pie Chart"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Circular Pie Chart` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/circular-pie-chart?lang=en>
:::

Another form of the pie chart.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/circular-pie-chart/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data$draw_percent <- data[["values"]] / sum(data[["values"]]) * 100
data$draw_class <- 1
data2 <- data
data2[["values"]] <- 0
data2$draw_class <- 0
data <- rbind(data, data2)
filtered_data <- data[data[["values"]] > 0,]

# View data
head(data)
```

## Visualization

```{r fig-1Circular-pie-chart}
#| label: fig-1Circular-pie-chart
#| fig-cap: "Circular Pie Chart"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 6
#| warning: false
#| message: false

# Circular Pie Chart
p <- ggplot(data, aes(x = draw_class, y = values, fill = labels)) +
  geom_bar(position = "stack", stat = "identity", width = 0.7) +
  geom_text(data = filtered_data, aes(label = sprintf("%.2f%%", draw_percent)),
            position = position_stack(vjust = 0.5), size = 3) +
  coord_polar(theta = "y") +
  xlab("") +
  ylab("Pie Chart") +
  scale_fill_manual(values = c("#e64b35ff","#4dbbd5ff","#00a087ff","#3c5488ff","#f39b7fff")) +
  theme_minimal() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(color = "black"),
        axis.text.y = element_blank(),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

p
```

