---
title: "Complex Heatmap"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Complex Heatmap` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/complex-heatmap?lang=en>
:::

A multi-omics plugins to draw heatmap, meta annotation, and mutations.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ComplexHeatmap`; `circlize`; `randomcoloR`; `ggplotify`; `stringr`; `cowplot`; `hiplotlib`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ComplexHeatmap", quietly = TRUE)) {
  BiocManager::install("ComplexHeatmap")
}
if (!requireNamespace("circlize", quietly = TRUE)) {
  install.packages("circlize")
}
if (!requireNamespace("randomcoloR", quietly = TRUE)) {
  install.packages("randomcoloR")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}
if (!requireNamespace("stringr", quietly = TRUE)) {
  install.packages("stringr")
}
if (!requireNamespace("cowplot", quietly = TRUE)) {
  install.packages("cowplot")
}
if (!requireNamespace("hiplotlib", quietly = TRUE)) {
  remotes::install_github("hiplot/hiplotlib")
}

# Load packages
library(data.table)
library(jsonlite)
library(ComplexHeatmap)
library(circlize)
library(randomcoloR)
library(ggplotify)
library(stringr)
library(cowplot)
library(hiplotlib)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/complex-heatmap/data.json")$exampleData[[1]]$textarea[[1]])
data <- as.data.frame(data)
data2 <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/complex-heatmap/data.json")$exampleData[[1]]$textarea[[2]])
data2 <- as.data.frame(data2)

# convert data structure
keep_vars_ref <- ls() 
row.names(data) <- data[, 1]
data <- data[, -1]
axis_raw <- c("KRAS","GBP4")
exp_start_col <- which(colnames(data) == axis_raw[2])
mut_start_col <- which(colnames(data) == axis_raw[1])
heat_mat <- as.matrix(t(data[, exp_start_col:ncol(data)]))
mut_mat <- as.matrix(t(data[, mut_start_col:(exp_start_col - 1)]))
mut_mat[is.na(mut_mat)] <- ""

color_key <- c("#196ABD", "#3399FF", "#3399FF", "#f4f4f4", "#f4f4f4", "#f4f4f4", "#FF3333", "#FF3333", "#C20B01")

cols <- c()
for (i in 1:nrow(data2)) {
  cols[data2[i,1]] <- data2[i,2]
}
col_meta <- list()
col_meta_pre <- list()
items <- c()
for (i in 1:(mut_start_col - 1)) {
  ref <- unique(data[, i])
  ref <- ref[!is.na(ref) & ref != ""]
  if (any(is.numeric(ref)) & length(ref) > 2) {
    col_meta_pre[[colnames(data)[i]]] <- hiplotlib::col_fun_cont(data[,i])
  } else if (length(ref) == 2 & any(is.numeric(ref))) {
    col_meta_pre[[colnames(data)[i]]] <- c("#f4f4f4", "#5a5a5a")
    items <- c(items, ref)
  } else if (length(ref) == 2 & any(is.character(ref))) {
    col_meta_pre[[colnames(data)[i]]] <- c("#196ABD", "#C20B01")
    items <- c(items, unique(data[, i]))
  } else if (length(unique(data[, i])) > 2) {
    col_meta_pre[[colnames(data)[i]]] <- distinctColorPalette(
      length(unique(data[, i]))
    )
    items <- c(items, unique(data[, i]))
  }
}
meta_mat2 <- NULL
meta_mat2_unique_names <- c()
meta_mat2_unique_cols <- c()
for (i in names(col_meta_pre)) {
  if (!is.function(col_meta_pre[[i]])) {
    meta_mat2_unique_names <- c(meta_mat2_unique_names, i)
    meta_mat2_unique_cols <- c(meta_mat2_unique_cols, col_meta_pre[[i]])
    meta_mat2 <- cbind(meta_mat2, data[, i])
    colnames(meta_mat2)[ncol(meta_mat2)] <- i
  } else {
    col_meta[[i]] <- col_meta_pre[[i]]
  }
}
meta_mat2 <- as.matrix(meta_mat2)
col_meta[["Meta2"]] <- structure(
  names = items[!duplicated(items)],
  meta_mat2_unique_cols[!duplicated(items)]
)

# View data
head(data)
```

## Visualization

```{r fig-1Complex-heatmap}
#| label: fig-1Complex-heatmap
#| fig-cap: "Complex Heatmap"
#| out.width: "95%"
#| fig-height: 10
#| fig-width: 8
#| warning: false
#| message: false

# Complex Heatmap
params <- list()
for (i in names(col_meta)) {
  if (i != "Meta2") {
    params[[i]] <- data[, i]
  }
}
params2 <- list(
  Meta2 = meta_mat2,
  gap = 0,
  border = TRUE,
  show_annotation_name = TRUE,
  col = col_meta,
  na_col = "#FFFFFF",
  show_legend = FALSE,
  annotation_legend_param = list(direction = "horizontal")
)
for (i in names(params2)) {
  params[[i]] <- params2[[i]]
}
ha <- do.call(HeatmapAnnotation, params)
hlist <- Heatmap(heat_mat,
      col = hiplotlib::col_fun_cont(heat_mat, cols = color_key),
      name = "Expression",
      gap = 0,
      clustering_distance_columns = "euclidean",
      clustering_distance_rows = "euclidean",
      clustering_method_columns = "ward.D2",
      show_row_dend = TRUE, show_column_dend = TRUE,
      show_row_names = FALSE,
      row_title_gp = gpar(col = "#FFFFFF00"),
      cluster_rows = TRUE,
      cluster_columns = TRUE,
      bottom_annotation = ha,
      show_heatmap_legend = TRUE,
      heatmap_legend_param = list(direction = "horizontal")
    )
p1 <- as.ggplot(
  function() {
    draw(hlist, annotation_legend_side = "right", heatmap_legend_side = "top")
  }
)
idx <- sort(rowSums(!is.na(mut_mat) & mut_mat != "0" & mut_mat != ""), decreasing = TRUE)
mut_mat <- mut_mat[names(idx),]

p2 <- as.ggplot(
  function() {
    params <- list(
      mut_mat,
      get_type = function(x) strsplit(x, "/")[[1]],
      alter_fun = hiplotlib::alter_fun, col = cols, row_order = 1:nrow(mut_mat),
      show_column_names = TRUE,
      show_pct = TRUE,
      right_annotation = NULL,
      top_annotation = NULL,
      border = TRUE,
      heatmap_legend_param = list(direction = "horizontal"),
      show_heatmap_legend = FALSE)
      params$column_order <- unlist(column_order(hlist))
      draw(do.call(oncoPrint, params), annotation_legend_side = "bottom", heatmap_legend_side = "bottom")
    }
  )

p3 <- as.ggplot(function() {
    legend_tmp <- list()
    for (i in names(col_meta_pre)) {
      if (is.function(col_meta_pre[[i]])) {
        legend_tmp[[i]] <- Legend(
          col_fun = col_meta_pre[[i]],
          title = i, direction = "horizontal"
        )
      } else if (identical(col_meta_pre[[i]], c("#f4f4f4", "#5a5a5a"))) {
        legend_tmp[[i]] <- Legend(
          at = unique(data[, i]), title = i,
          direction = "horizontal",
          labels = c("No", "Yes"),
          legend_gp = gpar(fill = col_meta_pre[[i]])
        )
      } else {
         legend_tmp[[i]] <- Legend(
          at = unique(data[, i]), title = i,
          direction = "horizontal",
          legend_gp = gpar(fill = col_meta_pre[[i]])
        )
      }
    }
    ref_mut <- unique(unlist(str_split(mut_mat, "/")))
    ref_mut <- ref_mut[ref_mut != "" & ref_mut != "NANA"]
    ref_mut <- ref_mut[!is.na(ref_mut)]
    lgd_mut <- Legend(
      at = ref_mut, title = "Mutations",
      direction = "horizontal",
      legend_gp = gpar(fill = cols[ref_mut])
    )
    legend_tmp[[length(legend_tmp) + 1]] <- lgd_mut
    legend_tmp$direction <- "horizontal"
    legend_tmp$max_width <- unit(14, "cm")
    legend_tmp$column_gap <- unit(5, "mm")
    legend_tmp$row_gap <- unit(0.5, "cm")
    draw(do.call(packLegend, legend_tmp))
  })
rel_height <- as.numeric(str_split("4, 2, 2", ", |,| |;")[[1]])
p <- plot_grid(p1, p2, p3, ncol = 1, rel_heights = rel_height)
p
```



