---
title: "Contour (XY)"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Contour (XY)` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/contour-xy?lang=en>
:::

Contour plot (XY) is a data processing method that reflects data density through contour line.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `ggisoband`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("ggisoband", quietly = TRUE)) {
  remotes::install_github("clauswilke/ggisoband")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(ggisoband)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data are two variables.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/contour-xy/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
colnames(data) <- c("xvalue", "yvalue")

# View data
head(data)
```

## Visualization

```{r fig-1Contour-xy}
#| label: fig-1Contour-xy
#| fig-cap: "Contour (XY)"
#| out.width: "95%"
#| fig-height: 2.5
#| fig-width: 4
#| warning: false
#| message: false

# Contour (XY)
p <- ggplot(data, aes(xvalue, yvalue)) +
  geom_density_bands(
    alpha = 1,
    aes(fill = stat(density)), color = "gray40", size = 0.2
    ) +
  geom_point(alpha = 1, shape = 21, fill = "white") +
  scale_fill_viridis_c(guide = "legend") +
  ylab("value2") +
  xlab("value1") +
  ggtitle("Contour-XY Plot") +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

Just as contour lines in geography represent different heights, different contour lines in contour maps represent different densities. The closer to the center, the smaller contour loop is, and the higher the regional data density is. For example, the data density of yellow area is the highest, while that of blue area is the lowest.
