---
title: "Simplified Correlation Heatmap"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Simplified Correlation Heatmap` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/cor-heatmap-simple?lang=en>
:::

Simplified variables correlation heatmap

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `ggisoband`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("sigminer", quietly = TRUE)) {
  BiocManager::install("sigminer")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(sigminer)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/cor-heatmap-simple/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1Cor-heatmap-simple}
#| label: fig-1Cor-heatmap-simple
#| fig-cap: "Simplified Correlation Heatmap"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 6
#| warning: false
#| message: false

# Simplified Correlation Heatmap
p <- show_cor(
  data = data,
  x_vars = c("mpg","cyl","disp"),
  y_vars = c("wt","hp","drat"),
  cor_method = "pearson",
  vis_method = "square",
  lab = T,
  test = T,
  hc_order = F,
  legend.title = "Corr"
  ) +
  ggtitle("") +
  labs(x="", y="") +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

