---
title: "Correlation Heatmap"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Correlation Heatmap` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/cor-heatmap?lang=en>
:::

The correlation heat map is a graph that analyzes the correlation between two or more variables.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggcorrplot`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggcorrplot", quietly = TRUE)) {
  install.packages("ggcorrplot")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggcorrplot)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data are the gene names and the expression of each sample.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/cor-heatmap/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data <- data[!is.na(data[, 1]), ]
idx <- duplicated(data[, 1])
data[idx, 1] <- paste0(data[idx, 1], "--dup-", cumsum(idx)[idx])
rownames(data) <- data[, 1]
data <- data[, -1]
str2num_df <- function(x) {
  final <- NULL
  for (i in seq_len(ncol(x))) {
    final <- cbind(final, as.numeric(x[, i]))
  }
  colnames(final) <- colnames(x)
  return(final)
}
tmp <- str2num_df(t(data))
corr <- round(cor(tmp, use = "na.or.complete", method = "pearson"), 3)
p_mat <- round(cor_pmat(tmp, method = "pearson"), 3)

# View data
head(data)
```

## Visualization

```{r fig-1Cor-heatmap}
#| label: fig-1Cor-heatmap
#| fig-cap: "Correlation Heatmap"
#| out.width: "95%"
#| fig-height: 9
#| fig-width: 9
#| warning: false
#| message: false

# Correlation Heatmap
p <- ggcorrplot(
  corr,
  colors = c("#4477AA", "#FFFFFF", "#BB4444"),
  method = "circle",
  hc.order = T,
  hc.method = "ward.D2",
  outline.col = "white",
  ggtheme = theme_bw(),
  type = "upper",
  lab = F,
  lab_size = 3,
  legend.title = "Correlation"
  ) +
  ggtitle("Cor Heatmap Plot") +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))
p
```

Red indicates positive correlation between two genes, blue indicates negative correlation between two genes, and the number in each cell indicates correlation coefficient.




