---
title: "Custom Heatmap"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Custom Heatmap` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/custom-heat-map?lang=en>
:::

Custom Heatmap, directly plot a heatmap based on the given data.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The case data is a grayscale image of the official logo of hiplot.org.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/custom-heat-map/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
draw_data <- as.matrix(data[, 2:ncol(data)])
row_num <- nrow(draw_data)
col_num <- ncol(draw_data)
col_labels <- colnames(data)
col_labels <- col_labels[2:ncol(data)]
row_labels <- data$name
rm(data)
df <- expand.grid(row = 1:row_num, col = 1:col_num)
df$value <- c(draw_data)

# View data
head(df)
```

## Visualization

```{r fig-1Custom-heat-map}
#| label: fig-1Custom-heat-map
#| fig-cap: "Custom Heatmap"
#| out.width: "95%"
#| fig-height: 15
#| fig-width: 25
#| warning: false
#| message: false

# Custom Heatmap
p <- ggplot(df, aes(x = col, y = row, fill = value)) +
  geom_point(shape = 21, size = 8, aes(fill = value), color = "white") +
  scale_fill_gradient(low = "#DDDDDD", high = "#0000F5") +
  guides(fill = guide_colorbar(title = "Value")) +
  theme(
    panel.background = element_rect(fill = "white"),
    panel.grid = element_blank(),
    axis.text = element_text(size = 10),
    axis.ticks = element_blank(),
    axis.title = element_blank()
    ) +
  scale_x_continuous(breaks = 1:col_num, labels = col_labels, position = "top") +
  scale_y_reverse(breaks = 1:row_num, labels = row_labels, position = "left")

p
```



