---
title: "Dendrogram"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Dendrogram` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/dendrogram?lang=en>
:::

The dendrogram is a diagram representing a tree. This diagrammatic representation is frequently used in different contexts:In hierarchical clustering, it illustrates the arrangement of the clusters produced by the corresponding analyses.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ape`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ape", quietly = TRUE)) {
  install.packages("ape")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(data.table)
library(jsonlite)
library(ape)
library(ggplotify)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/dendrogram/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data <- data[, -1]

# View data
head(data)
```

## Visualization

```{r fig-1Dendrogram}
#| label: fig-1Dendrogram
#| fig-cap: "Dendrogram"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 6
#| warning: false
#| message: false

# Dendrogram
d <- dist(t(data), method = "euclidean")
hc <- hclust(d, method = "complete")
clus <- cutree(hc, 4)

p <- as.ggplot(function() {
  par(mar = c(5, 5, 10, 5), mgp = c(2.5, 1, 0))
  plot(as.phylo(hc),
       type = "phylogram",
       tip.color = c("#00468bff","#ed0000ff","#42b540ff","#0099b4ff")[clus], 
       label.offset = 1,
       cex = 1, font = 2, use.edge.length = T
       )
  title("Dendrogram Plot", line = 1)
  })

p
```

