---
title: "Diffusion Map"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Diffusion Map` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/diffusion-map?lang=en>
:::

Diffusion Map is a nonlinear dimensionality reduction algorithm that can be used to visualize developmental trajectories.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `destiny`; `ggplotify`; `scatterplot3d`; `ggpubr`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("destiny", quietly = TRUE)) {
  install.packages("https://github.com/theislab/destiny/archive/refs/tags/v3.1.1.tar.gz")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}
if (!requireNamespace("scatterplot3d", quietly = TRUE)) {
  install.packages("scatterplot3d")
}
if (!requireNamespace("ggpubr", quietly = TRUE)) {
  install.packages("ggpubr")
}

# Load packages
library(data.table)
library(jsonlite)
library(destiny)
library(ggplotify)
library(scatterplot3d)
library(ggpubr)
library(smoother)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data1 <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/diffusion-map/data.json")$exampleData[[1]]$textarea[[1]])
data1 <- as.data.frame(data1)
data2 <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/diffusion-map/data.json")$exampleData[[1]]$textarea[[2]])
data2 <- as.data.frame(data2)

# convert data structure
sample.info <- data2
rownames(data1) <- data1[, 1]
data1 <- as.matrix(data1[, -1])
## tsne
set.seed(123)
dm_info <- DiffusionMap(t(data1))
dm_info <- cbind(DC1 = dm_info$DC1, DC2 = dm_info$DC2, DC3 = dm_info$DC3)
dm_data <- data.frame(
  sample = colnames(data1),
  dm_info
)

colorBy <- sample.info[match(colnames(data1), sample.info[, 1]), "Group"]
colorBy <- factor(colorBy, level = colorBy[!duplicated(colorBy)])
dm_data$colorBy = colorBy

# View data
head(dm_data)
```

## Visualization

### 1. 2D

```{r fig-1Diffusion-map2D}
#| label: fig-1Diffusion-map2D
#| fig-cap: "2D Diffusion Map"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 5
#| warning: false
#| message: false

# 2D Diffusion Map
p <- ggscatter(data = dm_data,  x = "DC1", y = "DC2", color = "colorBy",
               size = 2, palette = "lancet", alpha = 1) +
  labs(color = "Group") +
  ggtitle("Diffusion Map") +
  scale_color_manual(values = c("#3B4992FF","#EE0000FF","#008B45FF")) +
  theme_classic() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```


### 2. 3D

```{r fig-2Diffusion-map3D}
#| label: fig-2Diffusion-map3D
#| fig-cap: "3D Diffusion Map"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 8
#| warning: false
#| message: false

# 3D Diffusion Map
group.color <- c("#3B4992FF","#EE0000FF","#008B45FF")
names(group.color) <- unique(dm_data$colorBy)
group.color <- group.color[!is.na(names(group.color))]
if (length(group.color) == 0) {
  group.color <- c(Default="black")
  dm_data$colorBy <- "Default"
}
p <- as.ggplot(function(){
  scatterplot3d(x = dm_data$DC1, y = dm_data$DC2, z = dm_data$DC3,
                color =  alpha(group.color[dm_data$colorBy], 1),
                xlim=c(min(dm_data$DC1), max(dm_data$DC1)),
                ylim=c(min(dm_data$DC2), max(dm_data$DC2)),
                zlim=c(min(dm_data$DC3), max(dm_data$DC3)),
                pch = 16, cex.symbols  = 0.6,
                scale.y = 0.8,
                xlab = "DC1", ylab = "DC2", zlab = "DC3",
                angle = 40,
                main = "Diffusion Map",
                col.axis = "#444444", col.grid = "#CCCCCC")
  legend("right", legend = names(group.color),
         col = alpha(group.color, 0.8), pch = 16)
    })
p <- p + theme_classic()

p
```

