---
title: "Dual Y Axis Chart"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Dual Y Axis Chart` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/dual-y-axis?lang=en>
:::

The dual Y-axis graph can put two groups of data with larger orders of magnitude in the same graph for display.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data is divided into three columns, the first column is the value of the x-axis, the second column is the value of the left Y-axis, and the third column is the value of the right Y-axis.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/dual-y-axis/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1Dual-y-axis}
#| label: fig-1Dual-y-axis
#| fig-cap: "Dual Y Axis Chart"
#| out.width: "95%"
#| fig-height: 3
#| fig-width: 4
#| warning: false
#| message: false

# Dual Y Axis Chart
p <- ggplot(data, aes(x = x)) +
  geom_line(aes(y = data[, 2]), size = 1, color = "#D72C15") +
  geom_line(aes(y = data[, 3] / as.numeric(10)), size = 1, color = "#02657B") +
  scale_y_continuous(
    name = colnames(data)[2],
    sec.axis = sec_axis(~ . * as.numeric(10), name = colnames(data)[3])) +
  ggtitle("Dual Y Axis Chart") + xlab("x") +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

Interpretation of case statistics graphics
In the case data, the Y-axis scale on the left is in the range of 0-100, while the Y-axis scale on the right is 0-1000.

