---
title: "Dumbbell Chart"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Dumbbell Chart` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/dumbbell?lang=en>
:::

Dumbbell Chart can display the data change.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `ggalt`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("ggalt", quietly = TRUE)) {
  remotes::install_github("hrbrmstr/ggalt")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(ggalt)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/dumbbell/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1Dumbbell}
#| label: fig-1Dumbbell
#| fig-cap: "Dumbbell Chart"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 7
#| warning: false
#| message: false

# Dumbbell Chart
colors <- c("#3B4992FF","#EE0000FF")
p <- ggplot(data, aes(y = reorder(country, y1952), x = y1952, xend = y2007)) +
  geom_dumbbell(size = 1, size_x = 3,  size_xend = 3, colour = "#AFAFAF",  
                colour_x = colors[1],  colour_xend = colors[2]) +
  labs(title = "Dummbbell Chart", x = "Life Expectancy (years)",
       y = "country") +
  theme_minimal() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```


