---
title: "Easy Pairs"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Easy Pairs` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/easy-pairs?lang=en>
:::

Display a matrix of plots for viewing correlation relationship and distributions of multiple variables.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `GGally`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("GGally", quietly = TRUE)) {
  install.packages("GGally")
}

# Load packages
library(data.table)
library(jsonlite)
library(GGally)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/easy-pairs/data.json")$exampleData[[1]]$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1Easy-pairs}
#| label: fig-1Easy-pairs
#| fig-cap: "Easy Pairs"
#| out.width: "95%"
#| fig-height: 8
#| fig-width: 8
#| warning: false
#| message: false

# Easy Pairs
p <- ggpairs(data, columns = c("total_bill", "time", "tip"),
             mapping = aes_string(color = "gender")) +
  ggtitle("Easy Pairs") +
  scale_fill_manual(values = c("#3B4992FF","#EE0000FF")) +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```


