---
title: "Extended Scatter"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Extended Scatter` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/extended-scatter?lang=en>
:::

An extended scatter plot adds marginal plots to the basic scatter plot to provide a more comprehensive view of the data distribution.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `ggExtra`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("ggExtra", quietly = TRUE)) {
  install.packages("ggExtra")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(ggExtra)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/extended-scatter/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1Eulerr}
#| label: fig-1Eulerr
#| fig-cap: "Extended Scatter"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 6
#| warning: false
#| message: false

# Extended Scatter
p <- ggplot(data, aes(x = wt, y = mpg, color = cyl, size = cyl)) +
  geom_point() +
  geom_rug(alpha = 0.2, size = 1.5, col = "#4f80b3") +
  theme(legend.position = "none")

p <- ggMarginal(
  p, type = "densigram", fill = "#7054cc", color = "#7f0080",
  size = 4, bins = 30)

p
```


