---
title: "Flower plot"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Flower plot` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/flowerplot?lang=en>
:::

Flower plot with multiple sets.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `flowerplot`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("flowerplot", quietly = TRUE)) {
  remotes::install_github("dongwei1220/flowerplot")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(data.table)
library(jsonlite)
library(flowerplot)
library(ggplotify)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/flowerplot/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1Flowerplot}
#| label: fig-1Flowerplot
#| fig-cap: "Flower plot"
#| out.width: "95%"
#| fig-height: 7
#| fig-width: 7
#| warning: false
#| message: false

# Flower plot
p <- as.ggplot(function(){
  flowerplot(
    flower_dat = data,
    angle = 90,
    a = 0.5,
    b = 2,
    r = 1,
    ellipse_col = "RdBu",
    circle_col = "#FFFFFF",
    label_text_cex = 1
  )})

p
```
