---
title: "Funnel Plot (metafor)"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Funnel Plot (metafor)` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/funnel-plot-metafor?lang=en>
:::

Can be used to show potential bias factors in Meta-analysis.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `metafor`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("metafor", quietly = TRUE)) {
  install.packages("metafor")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(data.table)
library(jsonlite)
library(metafor)
library(ggplotify)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/funnel-plot-metafor/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data2 <- escalc(ri=ri, ni=ni, data = data, measure="ZCOR")
res <- rma(yi, vi, data = data2)

# View data
head(data)
```

## Visualization

```{r fig-1Funnel-plot-metafor}
#| label: fig-1Funnel-plot-metafor
#| fig-cap: "Funnel Plot"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 8
#| warning: false
#| message: false

# Funnel Plot
p <- as.ggplot(function(){
  funnel(x = res, main = "Funnel Plot (metafor)",
         level = c(90, 95, 99), shade = c("white","#a90e07","#d23e0b"), refline = 0)
  })

p
```

