---
title: "Gene Density"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Gene Density` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/gene-density?lang=en>
:::

Chrosome data visualization.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `circlize`; `ComplexHeatmap`; `gtrellis`; `tidyverse`; `ggplotify`; `RColorBrewer`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("circlize", quietly = TRUE)) {
  install.packages("circlize")
}
if (!requireNamespace("ComplexHeatmap", quietly = TRUE)) {
  BiocManager::install("ComplexHeatmap")
}
if (!requireNamespace("gtrellis", quietly = TRUE)) {
  remotes::install_github("jokergoo/gtrellis")
}
if (!requireNamespace("tidyverse", quietly = TRUE)) {
  install.packages("tidyverse")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}
if (!requireNamespace("RColorBrewer", quietly = TRUE)) {
  install.packages("RColorBrewer")
}

# Load packages
library(data.table)
library(jsonlite)
library(circlize)
library(ComplexHeatmap)
library(gtrellis)
library(tidyverse)
library(ggplotify)
library(RColorBrewer)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data1 <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/gene-density/data.json")$exampleData$textarea[[1]])
data1 <- as.data.frame(data1)
data2 <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/gene-density/data.json")$exampleData$textarea[[2]])
data2 <- as.data.frame(data2)

# Convert data structure
chrNum <- str_replace(unique(data1$chr), "Chr|chr", "")
data1$chr <- factor(data1$chr, levels = paste0("Chr", chrNum))
data2$chr <- factor(data2$chr, levels = paste0("Chr", chrNum))
# Set window to calculate gene density
windows <- 100 * 1000 # default:100kb window size
gene_density <- genomicDensity(data2, window.size = windows)
gene_density$chr <- factor(gene_density$chr,
  levels =  paste0("Chr", chrNum)
)

# View data
head(data1)
head(data2)
```

## Visualization

```{r fig-1Gene-density}
#| label: fig-1Gene-density
#| fig-cap: "Gene Density"
#| out.width: "95%"
#| fig-height: 3
#| fig-width: 7
#| warning: false
#| message: false

# Set the palettes
palettes <- c("#B2182B","#EF8A62","#FDDBC7","#D1E5F0","#67A9CF","#2166AC")
col_fun <- colorRamp2(
  seq(0, max(gene_density[[4]]), length = 6), rev(palettes)
  )
cm <- ColorMapping(col_fun = col_fun)
# Set the Legend
lgd <- color_mapping_legend(
  cm, plot = F, title = "density", color_bar = "continuous"
  )
# Plot
p <- as.ggplot(function() {
  gtrellis_layout(
    data1, n_track = 2, ncol = 1, byrow = FALSE,
    track_axis = FALSE, add_name_track = FALSE,
    xpadding = c(0.1, 0), gap = unit(1, "mm"),
    track_height = unit.c(unit(1, "null"), unit(4, "mm")),
    track_ylim = c(0, max(gene_density[[4]]), 0, 1),
    border = FALSE, asist_ticks = FALSE,
    legend = lgd
    )
  # Add gene area map track
  add_lines_track(gene_density, gene_density[[4]],
                  area = TRUE, gp = gpar(fill = "pink"))
  # Add gene density heatmap track
  add_heatmap_track(gene_density, gene_density[[4]], fill = col_fun)
  add_track(track = 2, clip = FALSE, panel_fun = function(gr) {
    chr <- get_cell_meta_data("name")
    if (chr == paste("Chr", length(chrNum), sep = "")) {
      grid.lines(get_cell_meta_data("xlim"), unit(c(0, 0), "npc"),
                 default.units = "native")
      }
    grid.text(chr, x = 0.01, y = 0.38, just = c("left", "bottom"))
    })
  circos.clear()
  })

p
```


