---
title: "Gene Ranking Dotplot"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Gene Ranking Dotplot` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/gene-rank?lang=en>
:::

Gene expression ranking visualization.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggrepel`; `ggplot2`; `RColorBrewer`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggrepel", quietly = TRUE)) {
  install.packages("ggrepel")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("RColorBrewer", quietly = TRUE)) {
  install.packages("RColorBrewer")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggrepel)
library(ggplot2)
library(RColorBrewer)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/gene-rank/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
## ordered by log2FoldChange and pvalue
data <- data[order(-data$log2FC, data$pvalue), ]
## add the rank column
data$rank <- 1:nrow(data)
## get the top n up and down gene for labeling
top_n <- 5
top_n_up <- rownames(head(data, top_n))
top_n_down <- rownames(tail(data, top_n))
genes_to_label <- c(top_n_up, top_n_down)
data2 <- data[genes_to_label, ]

# View data
head(data)
```

## Visualization

```{r fig-1Gene-rank}
#| label: fig-1Gene-rank
#| fig-cap: "Gene Ranking Dotplot"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 6
#| warning: false
#| message: false

# Gene Ranking Dotplot
p <- 
  ggplot(data, aes(rank, log2FC, color = pvalue, size = abs(log2FC))) + 
  geom_point() + 
  scale_color_gradientn(colours = colorRampPalette(brewer.pal(11,'RdYlBu'))(100)) +
  geom_hline(yintercept = c(-1, 1), linetype = 2, size = 0.3) +
  geom_hline(yintercept = 0, linetype = 1, size = 0.5) +
  geom_vline(xintercept = median(data$rank), linetype = 2, size = 0.3) + 
  geom_text_repel(data = data2, aes(rank, log2FC, label = gene),
                  size = 3, color = "red") +
  xlab("") + ylab("") + 
  ylim(c(-max(abs(data$log2FC)), max(abs(data$log2FC)))) +
  labs(color = "Pvalue", size = "Log2FoldChange") +
  theme_bw(base_size = 12) +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```



