---
title: "Gene Cluster Trend"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Gene Cluster Trend` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/gene-trend?lang=en>
:::

The gene cluster trend is used to display different gene expression trend with multiple lines showing the similar expression patterns in each cluster.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `Mfuzz`; `ggplotify`; `RColorBrewer`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("Mfuzz", quietly = TRUE)) {
  remotes::install_github("MatthiasFutschik/Mfuzz")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}
if (!requireNamespace("RColorBrewer", quietly = TRUE)) {
  install.packages("RColorBrewer")
}

# Load packages
library(data.table)
library(jsonlite)
library(Mfuzz)
library(ggplotify)
library(RColorBrewer)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data are a gene expression matrix with each row represent a gene and each column represent a time-point sample.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/gene-trend/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
## Convert a gene expression matrix to an ExpressionSet object
row.names(data) <- data[,1]
data <- data[,-1]
data <- as.matrix(data)
eset <- new("ExpressionSet", exprs = data)
## Filter genes with more than 25% missing values
eset <- filter.NA(eset, thres=0.25)
## Remove genes with small differences between samples based on standard deviation
eset <- filter.std(eset, min.std=0, visu = F)
## Data Standardization
eset <- standardise(eset)
## Set the number of clusters
c <- 6
## Evaluate the optimal m value
m <- mestimate(eset)
## Perform mfuzz clustering
cl <- mfuzz(eset, c = c, m = m)

# View data
head(data)
```

## Visualization

```{r fig-1Gene-trend}
#| label: fig-1Gene-trend
#| fig-cap: "Gene Cluster Trend"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 10
#| warning: false
#| message: false

# Gene Cluster Trend
p <- as.ggplot(function(){
  mfuzz.plot2(
  eset,
  cl,
  xlab = "Time",
  ylab = "Expression changes",
  mfrow = c(2,(c/2+0.5)),
  colo = "fancy",
  centre = T,
  centre.col = "red",
  time.labels = colnames(eset),
  x11=F)
  })

p
```

As shown in the example figure, the genes are clustered into different groups, with each group showing similar expression patterns across different time-points. The average expression trend is highlighted in each cluster.

