---
title: "Barstats"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Barstats` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/ggbarstats?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggstatsplot`; `ggplot2`; `cowplot`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggstatsplot", quietly = TRUE)) {
  install.packages("ggstatsplot")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("cowplot", quietly = TRUE)) {
  install.packages("cowplot")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggstatsplot)
library(ggplot2)
library(cowplot)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/ggbarstats/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
axis <- c("relig", "partyid", "race")
data[, axis[1]] <- factor(data[, axis[1]], levels = rev(unique(data[, axis[1]])))
data[, axis[2]] <- factor(data[, axis[2]], levels = unique(data[, axis[2]]))
data[, axis[3]] <- factor(data[, axis[3]], levels = unique(data[, axis[3]]))

# View data
head(data)
```

## Visualization

```{r fig-1ggbarstats}
#| label: fig-1ggbarstats
#| fig-cap: "Barstats"
#| out.width: "95%"
#| fig-height: 14
#| fig-width: 9
#| warning: false
#| message: false

# Barstats
g <- unique(data[,axis[3]])
plist <- list()
for (i in 1:length(g)) {
  fil <- data[,axis[3]] == g[i]
  plist[[i]] <- ggbarstats(
    data = data[fil,], x = relig, y = partyid,
    plotgrid.args = list(ncol = 1), paired = F, k = 2) +
    scale_fill_manual(values = c("#00468BFF","#ED0000FF","#42B540FF"))
}
p <- plot_grid(plotlist = plist, ncol = 1)

p
```


