---
title: "Betweenstats"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Betweenstats` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/ggbetweenstats?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggstatsplot`; `ggplot2`; `cowplot`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggstatsplot", quietly = TRUE)) {
  install.packages("ggstatsplot")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("cowplot", quietly = TRUE)) {
  install.packages("cowplot")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggstatsplot)
library(ggplot2)
library(cowplot)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/ggbetweenstats/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
axis <- c("mpaa", "length", "genre")
data[, axis[1]] <- factor(data[, axis[1]], levels = unique(data[, axis[1]]))
data[, axis[3]] <- factor(data[, axis[3]], levels = unique(data[, axis[3]]))

# View data
head(data)
```

## Visualization

```{r fig-1ggbarstats}
#| label: fig-1ggbarstats
#| fig-cap: "Betweenstats"
#| out.width: "95%"
#| fig-height: 10
#| fig-width: 10
#| warning: false
#| error: false
#| message: false

# Betweenstats
g <- unique(data[,axis[3]])
plist <- list()
for (i in 1:length(g)) {
  fil <- data[,axis[3]] == g[i]
  plist[[i]] <- ggbetweenstats(
    data = data[fil,], x = mpaa, y = length,
    title= paste('', axis[3], g[i], sep = ':'),
    p.adjust.method = "holm",
    plot.type = "boxviolin",
    pairwise.comparisons = T,
    pairwise.display = "significant",
    effsize.type = "unbiased",
    notch = T,
    type = "parametric",
    plotgrid.args = list(ncol = 2)) +
    scale_color_manual(values = c("#00468BFF","#ED0000FF","#42B540FF"))
}
p <- plot_grid(plotlist = plist, ncol = 2)

p
```

