---
title: "Scatterstats"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Scatterstats` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/ggscatterstats?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggpubr`; `ggthemes`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggstatsplot", quietly = TRUE)) {
  install.packages("ggstatsplot")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggstatsplot)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/ggscatterstats/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1ggpubr-boxplot}
#| label: fig-1ggpubr-boxplot
#| fig-cap: "Scatterstats"
#| out.width: "95%"
#| fig-height: 7
#| fig-width: 7
#| warning: false
#| error: false
#| message: false

# Scatterstats
p <- ggscatterstats(
  data = data, x = rating, y = budget
)

p
```



