---
title: "Seqlogo"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Seqlogo` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/ggseqlogo?lang=en>
:::

The sequence LOGO is a graphic that describes a sequence pattern of binding sites.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggseqlogo`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggseqlogo", quietly = TRUE)) {
  install.packages("ggseqlogo")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggseqlogo)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data is the Sequence of binding sites for multiple transcription factors on multiple genes.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/ggseqlogo/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data <- data[, !sapply(data, function(x) {all(is.na(x))})]
data <- as.list(data)
data <- lapply(data, function(x) {return(x[!is.na(x)])})

# View data
str(data[1:5])
```

## Visualization

```{r fig-1ggseqlogo}
#| label: fig-1ggseqlogo
#| fig-cap: "Seqlogo"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# Seqlogo
p <- ggseqlogo(
  data,
  ncol = 4,
  col_scheme = "nucleotide",
  seq_type = "dna",
  method = "bits") + 
  theme(plot.title = element_text(hjust = 0.5))

p
```

A sequence of binding sites was displayed in a column of the chart by means of BITS calculation, which could clearly observe the large proportion of bases of different sequences.


