---
title: "ggwordcloud"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `ggwordcloud` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/ggwordcloud?lang=en>
:::

The word cloud is to visualize the "keywords" that appear frequently in the web text by forming a "keyword cloud layer" or "keyword rendering".

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggwordcloud`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggwordcloud", quietly = TRUE)) {
  install.packages("ggwordcloud")
}
if (!requireNamespace("curl", quietly = TRUE)) {
  install.packages("curl")
}
if (!requireNamespace("png", quietly = TRUE)) {
  install.packages("png")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggwordcloud)
library(curl)
library(png)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

Load data nouns and noun frequencies.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/ggwordcloud/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)
inmask <- "https://download.hiplot.cn/api/file/fetch/?path=public/demo/ggwordcloud/hearth.png"

# Convert data structure
col <- data[, 2]
data <- cbind(data, col)

# View data
head(data)
```

## Visualization

```{r fig-1ggwordcloud}
#| label: fig-1ggwordcloud
#| fig-cap: "ggwordcloud"
#| out.width: "95%"
#| fig-height: 7
#| fig-width: 7
#| warning: false
#| error: false
#| message: false

# ggwordcloud
p <- ggplot(data, aes(label = word, size = freq, color = col)) +
  scale_size_area(max_size = 40) +
  theme_minimal() + 
  geom_text_wordcloud_area(
    mask = png::readPNG(curl::curl_fetch_memory(inmask)$content), 
    rm_outside = TRUE) +
  scale_color_gradient(low = "#8B0000", high = "#FF0000")

p
```

Display the proportion of nouns in the word cloud graph according to the frequency of nouns.


