---
title: "GOBar Plot"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `GOBar Plot` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/gobar?lang=en>
:::

The gobar plot is used to display Z-score coloured barplot of terms ordered alternatively by z-score or the negative logarithm of the adjusted p-value.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `GOplot`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("GOplot", quietly = TRUE)) {
  install.packages("GOplot")
}

# Load packages
library(data.table)
library(jsonlite)
library(GOplot)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data are the results of GO enrichment with seven columns: category, GO id, GO term, gene count, gene name, logFC, adjust pvalue and zscore.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/gobar/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
colnames(data) <- c("category","ID","term","count","genes","logFC","adj_pval","zscore")
data <- data[data$category %in% c("BP","CC","MF"),]
data <- data[!is.na(data$adj_pval),]
data$adj_pval <- as.numeric(data$adj_pval)
data$zscore <- as.numeric(data$zscore)

# View data
head(data)
```

## Visualization

```{r fig-1gobar}
#| label: fig-1gobar
#| fig-cap: "GOBar Plot"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 10
#| warning: false
#| error: false
#| message: false

# GOBar Plot
p <- GOBar(data, display = "multiple", order.by.zscore = T,
           title = "GO Enrichment Barplot ", 
           zsc.col = c("#EF8A62","#F7F7F7","#67A9CF")) + 
    theme(plot.title = element_text(hjust = 0.5),
          axis.text.x = element_text(size = 8))

p
```

As shown in the example figure, the x-axis represent each GO term, the y-axis represent the -log(adj_pvalue), each bar is colored by the z-score. If display is used to facet the plot the width of the panels will be proportional to the length of the x scale.


