---
title: "Group-comparison Heatmap"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Group-comparison Heatmap` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/group-comparison?lang=en>
:::

Group-comparison Heatmap provides a way to compare multiple variables across multiple (>2) groups and visualize the result with heatmap.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `sigminer`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("sigminer", quietly = TRUE)) {
  remotes::install_github("ShixiangWang/sigminer")
}

# Load packages
library(data.table)
library(jsonlite)
library(sigminer)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/group-comparison/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1group-comparison}
#| label: fig-1group-comparison
#| fig-cap: "Group-comparison Heatmap"
#| out.width: "95%"
#| fig-height: 2
#| fig-width: 3
#| warning: false
#| error: false
#| message: false

# Define plot functions
unlist_and_covert <- function(x, recursive = FALSE) {
  if (!is.null(x)) {
    x <- unlist(x, recursive = recursive)
    if (!is.null(x)) {
      y <- sapply(x, function(x) {
        if (identical(x, "NA")) NA else x
      })
      names(y) <- names(x)
      x <- y
    }
  }
  x
}

plotentry <- function(data,
                      grp_vars = NULL, enrich_vars = NULL, cross = TRUE,
                      co_method = c("t.test", "wilcox.test"), ref_group = NA,
                      scales = "free", add_text_annotation = TRUE,
                      fill_by_p_value = TRUE, use_fdr = TRUE, cut_p_value = FALSE,
                      cluster_row = FALSE) {
  ref_group <- unlist_and_covert(ref_group)
  if (is.null(ref_group)) ref_group <- NA
  rv <- group_enrichment(data, grp_vars, enrich_vars, cross, co_method, ref_group)
  if (length(unique(rv$grp_var)) == 1) {
    p <- show_group_enrichment(rv,
      return_list = TRUE,
      scales = scales, add_text_annotation = add_text_annotation,
      fill_by_p_value = fill_by_p_value, use_fdr = use_fdr, cut_p_value = cut_p_value,
      cluster_row = cluster_row
    )
    p <- p[[1]]
  } else {
    p <- show_group_enrichment(rv,
      scales = scales, add_text_annotation = add_text_annotation,
      fill_by_p_value = fill_by_p_value, use_fdr = use_fdr, cut_p_value = cut_p_value,
      cluster_row = cluster_row
    )
  }
  return(p)
}

# plot
p <- plotentry(
  data = data,
  grp_vars = "g1",
  enrich_vars = c("e1", "e2"),
  cross = T,
  add_text_annotation = T,
  fill_by_p_value = T,
  use_fdr = T,
  cut_p_value = F,
  cluster_row = F,
  co_method = "t.test",
  scales = "free"
)

p
```


