---
title: "Hi-C Heatmap"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Hi-C Heatmap` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/hic-heatmap?lang=en>
:::

The HiC heatmap is used to display the genome-wide chromatin interaction with heatmap on different chromosomes.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `RColorBrewer`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("RColorBrewer", quietly = TRUE)) {
  install.packages("RColorBrewer")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(RColorBrewer)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data have three columns, with the first for one locus bin index, the second for another locus bin index, and the third for the interaction frequency between this two locus.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/hic-heatmap/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1hic-heatmap}
#| label: fig-1hic-heatmap
#| fig-cap: "Hi-C Heatmap"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 6.5
#| warning: false
#| error: false
#| message: false

# Hi-C Heatmap
## Calculate the number of bins
bins_num <- max(data$index_bin1) + 1
## Set the resolution of HiC data
resolution <- 500
res <- resolution * 1000
# Set the separation unit to 50Mb
intervals <- 50
spacing <- intervals * 1000000
## Count the number of breaks
breaks_num <- (res * bins_num) / spacing
## Set breaks
breaks <- c()
for (i in 0:breaks_num) {
  breaks <- c(breaks, i * intervals)
}

p <- ggplot(data = data, aes(x = index_bin1 * res, y = index_bin2 * res)) +
  geom_tile(aes(fill = freq)) +
  scale_fill_gradientn(
    colours = colorRampPalette(rev(brewer.pal(11,"RdYlBu")))(500),
    limits = c(0, max(data$freq) * 1.2)
  ) +
  scale_y_reverse() +
  scale_x_continuous(breaks = breaks * 1000000, labels = paste0(breaks, "Mb")) +
  scale_y_continuous(breaks = breaks * 1000000, labels = paste0(breaks, "Mb")) +
  theme(panel.grid = element_blank(), axis.title = element_blank()) +
  labs(title = paste0("(resolution: ", res / 1000, "Kb)"), x="", y="") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "right", legend.key.size = unit(0.8, "cm"),
        panel.grid = element_blank())

p
```

As shown in the example figure, a heat map represent the interaction frequency between any two locus. The color displays their intensity of interaction.


