---
title: "Interval Area Chart"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Interval Area Chart` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/interval-area-chart?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The case data consists of the highest and lowest temperatures for each of the twelve months in a year, along with the corresponding abbreviated month names. Based on the case data, temperature intervals and average temperature lines have been plotted for each month.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/interval-area-chart/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data[["month"]] <- factor(data[["month"]], levels = data[["month"]])

# View data
head(data)
```

## Visualization

```{r fig-1interval-area-chart}
#| label: fig-1interval-area-chart
#| fig-cap: "Interval Area Chart"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 6
#| warning: false
#| error: false
#| message: false

# Interval Area Chart
p <- ggplot(data, aes(x = month, group = 1)) +
  geom_line(aes(y = max_temperature), size = 1.2, color = "#EA3323", 
            linetype = "solid") +
  geom_line(aes(y = min_temperature), size = 1.2, color = "#0000F5", 
            linetype = "solid") +
  geom_line(aes(x = month, y = mean), size = 1.2, color = "#BEBEBE", 
            linetype = "dashed") +
  geom_ribbon(aes(ymin = min_temperature, ymax = max_temperature), 
              fill = "#F2F2F2", alpha = 0.5) +
  geom_text(aes(x = month, y = max_temperature + 1, label = max_temperature),
            color = "#EA3323", size = 2.5, vjust = -0.5, hjust = 0) +
  geom_text(aes(x = month, y = min_temperature - 1, label = min_temperature),
            color = "#0000F5", size = 2.5, vjust = 1.5, hjust = 0) +
  geom_text(aes(x = month, y = mean, label = mean),
            color = "#BEBEBE", size = 2.5, vjust = 1.5, hjust = 0) +
  labs(title = "Temperature", x = "Month", y = "Temperature") +
  scale_color_manual(values = c(max = "#EA3323", min = "#0000F5")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

p
```



