---
title: "Interval Bar Chart"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Interval Bar Chart` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/interval-bar-chart?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The case data consists of the highest and lowest temperatures for each of the twelve months in a year, along with the corresponding abbreviated month names. Based on the case data, temperature intervals and average temperature lines have been plotted for each month.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/interval-bar-chart/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data$name_num <- match(data[["month"]], unique(data[["month"]]))

# View data
head(data)
```

## Visualization

```{r fig-1interval-bar-chart}
#| label: fig-1interval-bar-chart
#| fig-cap: "Interval Bar Chart"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 7
#| warning: false
#| error: false
#| message: false

# Interval Bar Chart
p <- ggplot(data, aes(x = month, y = max_temperature)) +
  geom_rect(aes(xmin = name_num - 0.4, xmax = name_num + 0.4,
                ymin = min_temperature, ymax = max_temperature), 
            fill = "#282726", alpha = 0.7) +
  geom_line(aes(x = name_num, y = mean), color = "#006064", size = 0.8) +
  labs(x = "Month", y = "Temperature") +
  scale_x_discrete() +
  theme_bw()

p
```



