---
title: "Likert Plot"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Likert Plot` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/likert?lang=en>
:::

Descriptive statistical analysis of Likert scale data.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplotify`; `likert`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}
if (!requireNamespace("likert", quietly = TRUE)) {
  install.packages("likert")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplotify)
library(likert)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/likert/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
levs <- unique(unlist(data))
for (i in 1:ncol(data)) {
  data[,i] <- factor(data[, i], levels = levs)
}

# View data
head(data)
```

## Visualization

```{r fig-1likert}
#| label: fig-1likert
#| fig-cap: "Likert Plot"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# Likert Plot
pobj <- likert(data)
colrs <- c("#3B4992FF","#EE0000FF")
p <- as.ggplot(plot(pobj, type = "bar", 
                    low.color = colrs[1], high.color = colrs[2], wrap = 50))

p
```


