---
title: "USA Map (County)"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `USA Map (County)` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/map-usa-county?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `RColorBrewer`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("RColorBrewer", quietly = TRUE)) {
  install.packages("RColorBrewer")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(RColorBrewer)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/map-usa-county/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)
dt_map <- readRDS(url("https://download.hiplot.cn/ui/basic/map-usa-county/usa.county.rds"))

# Convert data structure
dt_map$Value <- data$value[match(dt_map$county, data$name)]

# View data
head(data)
```

## Visualization

```{r fig-1map-usa-county}
#| label: fig-1map-usa-county
#| fig-cap: "USA Map (County)"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 6
#| warning: false
#| error: false
#| message: false

# USA Map (County)
p <- ggplot(dt_map) +
  geom_polygon(aes(x = long, y = lat, group = group, fill = Value),
               alpha = 0.9, size = 0.5) +
  geom_path(aes(x = long, y = lat, group = group), color = "black", size = 0.2) +
  coord_fixed() +
  scale_fill_gradientn(
    colours = colorRampPalette(rev(brewer.pal(11,"RdYlBu")))(500),
    breaks = seq(min(data$value), max(data$value), 
                 round((max(data$value)-min(data$value))/7)),
    name = "Color Key",
    guide = guide_legend(
      direction = "vertical", keyheight = unit(1, units = "mm"),
      keywidth = unit(8, units = "mm"),
      title.position = "top", title.hjust = 0.5, label.hjust = 0.5,
      nrow = 1, byrow = T, reverse = F, label.position = "bottom")) +
  theme(text = element_text(color = "#3A3F4A"),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 4 * 1.5, color = "black"),
        legend.title = element_text(size = 5 * 1.5, color = "black"),
        plot.title = element_text(
          face = "bold", size = 5 * 1.5, hjust = 0.5, 
          margin = margin(t = 4, b = 5), color = "black"),
        plot.background = element_rect(fill = "#FFFFFF", color = "#FFFFFF"),
        panel.background = element_rect(fill = "#FFFFFF", color = NA),
        legend.background = element_rect(fill = "#FFFFFF", color = NA),
        plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm")) +
  labs(x = NULL, y = NULL, title = "USA County Map")

p
```


