---
title: "World Map"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `World Map` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/map-world?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `RColorBrewer`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("RColorBrewer", quietly = TRUE)) {
  install.packages("RColorBrewer")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(RColorBrewer)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/map-world/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)
dt_map <- readRDS(url("https://download.hiplot.cn/ui/basic/map-world/world.rds"))

# Convert data structure
dt_map$Value <- data$death_rate[match(dt_map$ENG_NAME, data$region)]

# View data
head(data)
```

## Visualization

```{r fig-1map-world}
#| label: fig-1map-world
#| fig-cap: "World Map"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 6
#| warning: false
#| error: false
#| message: false

# World Map
p <- ggplot(dt_map) +
  geom_polygon(aes(x = long, y = lat, group = group, fill = Value),
               alpha = 0.9, size = 0.5) +
  geom_path(aes(x = long, y = lat, group = group), 
            color = "black", size = 0.2) +
  coord_fixed() +
  scale_fill_gradientn(
    colours = colorRampPalette(rev(brewer.pal(11,"RdYlBu")))(500),
    na.value = "grey10",
    limits = c(0, max(dt_map$Value) * 1.2)) +
    ggtitle("World Map Plot") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "bottom", legend.direction = "horizontal")

p
```


