---
title: "Meta-Subgroup Analysis"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Meta-Subgroup Analysis` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/metawho?lang=en>
:::

The goal of metawho is to provide simple R implementation of “Meta-analytical method to Identify Who Benefits Most from Treatments”.

metawho is powered by R package metafor and does not support dataset contains individuals for now. Please use stata package ipdmetan if you are more familar with stata code.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `meta`; `cowplot`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("metawho", quietly = TRUE)) {
  install.packages("metawho")
}
if (!requireNamespace("cowplot", quietly = TRUE)) {
  install.packages("cowplot")
}

# Load packages
library(data.table)
library(jsonlite)
library(metawho)
library(cowplot)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/metawho/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data = deft_prepare(data, conf_level = 1 - 0.95)
res = deft_do(data, group_level = unique(data$subgroup))

# View data
head(data)
```

## Visualization

```{r fig-1meta-cont}
#| label: fig-1metawho
#| fig-cap: "Meta-Subgroup Analysis"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# Meta-Subgroup Analysis
p1 <- deft_show(res, element = "all")
p2 <- deft_show(res, element = "subgroup")
p <- plot_grid(p1, p2, nrow = 2)

p
```


