---
title: "Moon charts"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Moon charts` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/moon-charts?lang=en>
:::

The moon chart is a graph that uses the moon's waxing and waning to reflect the size of the data.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `gggibbous`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("gggibbous", quietly = TRUE)) {
  install.packages("gggibbous")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(gggibbous)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data are the name of the restaurant and the number of types of food in the restaurant, the number of decorative style types, the number of tableware sets and the number of price types.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/moon-charts/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data[, 1] <- factor(data[, 1], levels = unique(data[, 1]))
rest_cols <- colnames(data)[-1]
tidyrest <- reshape(
  data,
  varying = rest_cols,
  v.names = "Score",
  timevar = "Category",
  times = factor(rest_cols, levels = rest_cols),
  idvar = colnames(data)[1],
  direction = "long"
)

# View data
head(data)
```

## Visualization

```{r fig-1moon-charts}
#| label: fig-1moon-charts
#| fig-cap: "Moon charts"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 7
#| warning: false
#| error: false
#| message: false

# Moon charts
p <- ggplot(tidyrest, aes(0, 0)) +
  geom_moon(aes(ratio = (Score - 1) / 4), fill = "black") +
  geom_moon(aes(ratio = 1 - (Score - 1) / 4), right = FALSE) +
  facet_grid(Category ~ Restaurant, switch = "y") +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank()
  )

p
```

The first row of the diagram shows the name of the restaurant, the first column shows different variables in the restaurant, the blank moon represents the number of 1 (the least number), the black moon represents the number of 5 (the most number) data, as the number of data increases, the black area of the moon gradually becomes larger, that is, gradually becomes full moon.



