---
title: "Network (igraph)"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Network (igraph)` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/network-igraph?lang=en>
:::

Network (igraph) can be used to visulize basic network based on igraph.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `igraph`; `stringr`; `ggplotify`; `RColorBrewer`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("igraph", quietly = TRUE)) {
  install.packages("igraph")
}
if (!requireNamespace("stringr", quietly = TRUE)) {
  install.packages("stringr")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}
if (!requireNamespace("RColorBrewer", quietly = TRUE)) {
  install.packages("RColorBrewer")
}

# Load packages
library(data.table)
library(jsonlite)
library(igraph)
library(stringr)
library(ggplotify)
library(RColorBrewer)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

Two data tables need to be entered. Table 1 is node information, including node ID and other annotation information, which can be used to map color and size. Table 2 is the link information, including node ID and connection information between nodes.

```{r load data, message=FALSE, warning=FALSE}
# Load data
nodes_data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/network-igraph/data.json")$exampleData[[1]]$textarea[[1]])
nodes_data <- as.data.frame(nodes_data)
edges_data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/network-igraph/data.json")$exampleData[[1]]$textarea[[2]])
edges_data <- as.data.frame(edges_data)

# Convert data structure
nodes_data[,"type.label"] <- factor(nodes_data[,"type.label"], 
                                    levels = unique(nodes_data[,"type.label"]))
nodes_data$hiplot_color_type <- as.numeric(nodes_data[,"type.label"])
net <- graph_from_data_frame(d = edges_data, vertices = nodes_data, directed = T)
## Generate colors based on type
colrs <- c("#7f7f7f","#ff6347","#ffd700")
colrs2 <- c("#BC3C29FF","#0072B5FF","#E18727FF","#20854EFF","#7876B1FF",
            "#6F99ADFF","#FFDC91FF","#EE4C97FF")
V(net)$color <- colrs[V(net)$hiplot_color_type]
## Compute node degrees (#links) and use that to set node size
deg <- degree(net, mode="all")
V(net)$size <- deg*3
## Set label
V(net)$label.color <- "black"
V(net)$label <- NA
## Set edge width based on weight
weight_column <- edges_data$weight
E(net)$width <- weight_column/6
## Change arrow size and edge color
E(net)$arrow.size <- .2
E(net)$edge.color <- "gray80"
edge.start <- ends(net, es=E(net), names=F)[,1]
edge.col <- V(net)$color[edge.start]

# View data
head(nodes_data)
head(edges_data)
```

## Visualization

```{r fig-1network-igraph}
#| label: fig-1network-igraph
#| fig-cap: "Network (igraph)"
#| out.width: "95%"
#| fig-height: 10
#| fig-width: 10
#| warning: false
#| error: false
#| message: false

# Network (igraph)
raw <- par()
p <- as.ggplot(function () {
  par(mar=c(8,2,2,2))
  radian.rescale <- function(x, start=0, direction=1) {
    c.rotate <- function(x) (x + start) %% (4 * pi) * direction
    c.rotate(scales::rescale(x, c(0, 2 * pi), range(x)))
  }

  label <- eval(parse(text = sprintf("V(net)$%s", "media")))

  l <- do.call(layout_as_star, list(net))
  params <- list(net, layout = l, main = "Network1",
      edge.color = edge.col, edge.curved = .1,
      vertex.shape = "circle",
      edge.lty = "solid",
      label.family = "Arial",
      vertex.label.family = "Arial",
      vertex.label.dist = 3.1,
      edge.arrow.mode = F
  )
  lab.locs <- radian.rescale(x=1:length(label), direction=-1, start=0)
  params$vertex.label.degree <- lab.locs
  params$vertex.label <- label
  params$vertex.color = V(net)$color
  do.call(plot, params)
  legend(x = -1.7, y = -1.4, unique(nodes_data[,"type.label"]), pch = 21,
        col = "#777777", pt.bg = colrs, pt.cex = 2, cex = .8, bty = "n",
        ncol = 1)
  legend(x = -1.2, y = -1.37,
    legend=round(sort(unique(E(net)$width)), 2), pt.cex= 0.8,
      col='black', ncol = 3, bty = "n", lty = 1,
      lwd = round(sort(unique(E(net)$width)), 2)
  )
  if (length(unique(V(net)$size)) > 8) {
    size_leg <- sort(unique(V(net)$size))[seq(1, length(unique(V(net)$size)), 2)]
  } else {
    size_leg <- sort(unique(V(net)$size))
  }
  legend(x = 0.5, y = -1.3,
        size_leg,
        pch = 21,
        col = "black", pt.bg = "#777777",
        pt.cex = size_leg / 3.8, cex = .8, bty = "n",
        ncol = 3,
        y.intersp = 3,
        x.intersp = 2.5,
        text.width = 0.25
  )
  par(mar=raw$mar)
})

p
```


