---
title: "Nomogram"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Nomogram` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/nomogram?lang=en>
:::

Nomogram is often used to evaluate the prognosis of oncology and medicine, and can visualize the results of logistic regression or Cox regression.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `survival`; `rms`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("survival", quietly = TRUE)) {
  install.packages("survival")
}
if (!requireNamespace("rms", quietly = TRUE)) {
  install.packages("rms")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(data.table)
library(jsonlite)
library(survival)
library(rms)
library(ggplotify)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

Survival data frame with time, which sex and status are presented by number such as 0,1 according to example data.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/nomogram/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
dd <- datadist(data)
options(datadist = "dd")
## Build COX model and run nomogram
cox_res <- psm(
  data = data,
  as.formula(paste(
    sprintf("Surv(%s, %s) ~ ", colnames(data)[1], colnames(data)[2]),
    paste(colnames(data)[3:length(colnames(data))],
      collapse = "+"
    )
  )),
  # Surv(time, status) ~ age + sex + ph.ecog + ph.karno + pat.karno,
  dist = "lognormal"
)
## Build survival probability function
surv <- Survival(cox_res)
## Build quantile survival time function
med <- Quantile(cox_res)

cox_nomo <- nomogram(
  cox_res,
  fun = list(function(x) surv(365, x), function(x) surv(1095, x),
             function(x) surv(1825, x), function(x) med(lp = x)),
  funlabel = c("1-year Survival Probability",
               "3-year Survival Probability",
               "5-year Survival Probability",
               "Median Survival Time"),
  maxscale = 100
)

# View data
head(data)
```

## Visualization

```{r fig-1nomogram}
#| label: fig-1nomogram
#| fig-cap: "Nomogram"
#| out.width: "95%"
#| fig-height: 9
#| fig-width: 12
#| warning: false
#| error: false
#| message: false

# Nomogram
p <- as.ggplot(function() {
  plot(cox_nomo, scale = 1)
  title(main = "Nomogram (COX)")
})

p
```


