---
title: "Pareto Chart"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Pareto Chart` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/pareto-chart?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The case data represents the sales data of a product on multiple platforms. The plugin will automatically plot a bar chart with sales data in descending order and simultaneously calculate the cumulative sales to draw the cumulative line chart.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/pareto-chart/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data <- data[order(-data[["sales"]]), ]
data[["channel"]] <- factor(data[["channel"]], levels = data[["channel"]])
## Calculate percentage number
data$accumulating <- cumsum(data[["sales"]])
max_y <- max(data[["sales"]])
cal_num <- sum(data[["sales"]]) / max_y
data$accumulating <- data$accumulating / cal_num

# View data
head(data)
```

## Visualization

```{r fig-1pareto-chart}
#| label: fig-1pareto-chart
#| fig-cap: "Pareto Chart"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# Pareto Chart
p <- ggplot(data, aes(x = channel, y = sales, fill = channel)) +
  geom_bar(stat = "identity") +
  geom_line(aes(y = accumulating), group = 1) +
  geom_point(aes(y = accumulating), show.legend = FALSE) +
  scale_y_continuous(sec.axis = sec_axis(trans = ~ . / max_y * 100, name = "Percentage")) +
  scale_fill_manual(values = c("#E64B35FF","#4DBBD5FF","#00A087FF","#3C5488FF",
                               "#F39B7FFF","#8491B4FF","#91D1C2FF","#DC0000FF")) +
  theme_bw()

p
```


