---
title: "PCAtools"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `PCAtools` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/pcatools?lang=en>
:::

PCAtools can reduce the dimensionality of data through principal component analysis, and view principal component related features at a two-dimensional level

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `PCAtools`; `ggplotify`; `cowplot`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("PCAtools", quietly = TRUE)) {
  install.packages('PCAtools', repos = c('https://bioc.r-universe.dev', 'https://cloud.r-project.org'))

}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}
if (!requireNamespace("cowplot", quietly = TRUE)) {
  install.packages("cowplot")
}

# Load packages
library(data.table)
library(jsonlite)
library(PCAtools)
library(ggplotify)
library(cowplot)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

- Data table 1 (numerical matrix):

Each column is a sample, and each row is a feature (such as gene, chip probe).

- Data sheet 2 (sample information):

The first column is the sample, and the other columns are the phenotypic characteristics of the sample, which can be used to mark the color and shape of the point and perform correlation analysis with the principal component.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/pcatools/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)
data2 <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/pcatools/data.json")$exampleData$textarea[[2]])
data2 <- as.data.frame(data2)

# View data
head(data[,1:5])
head(data2[,1:5])
```

## Visualization

```{r fig-1pcatools}
#| label: fig-1pcatools
#| fig-cap: "PCAtools"
#| out.width: "95%"
#| fig-height: 14
#| fig-width: 22
#| warning: false
#| error: false
#| message: false

# PCAtools
## Define the plot function
call_pcatools <- function(datTable, sampleInfo,
                          top_var,
                          screeplotComponents, screeplotColBar,
                          pairsplotComponents,
                          biplotShapeBy, biplotColBy,
                          plotloadingsComponents,
                          plotloadingsLowCol,
                          plotloadingsMidCol,
                          plotloadingsHighCol,
                          eigencorplotMetavars,
                          eigencorplotComponents) {
  row.names(datTable) <- datTable[, 1]
  datTable <- datTable[, -1]
  row.names(sampleInfo) <- sampleInfo[, 1]
  data3 <<- pca(datTable, metadata = sampleInfo, removeVar = (100 - top_var) / 100)

  for (i in c("screeplotComponents", "pairsplotComponents",
              "plotloadingsComponents", "eigencorplotComponents")) {
    if (ncol(data3$rotated) < get(i)) {
      assign(i, ncol(data3$rotated))
    }
  }

  p1 <- PCAtools::screeplot(
    data3,
    components = getComponents(data3, 1:screeplotComponents),
    axisLabSize = 14, titleLabSize = 20,
    colBar = screeplotColBar,
    gridlines.major = FALSE, gridlines.minor = FALSE,
    returnPlot = TRUE
  )

  params_pairsplot <- list(
    data3,
    components = getComponents(data3, c(1:pairsplotComponents)),
    triangle = TRUE, trianglelabSize = 12,
    hline = 0, vline = 0,
    pointSize = 0.8, gridlines.major = FALSE, gridlines.minor = FALSE,
    title = "", plotaxes = FALSE,
    margingaps = unit(c(0.01, 0.01, 0.01, 0.01), "cm"),
    returnPlot = TRUE,
    colkey = c("#00468BFF","#ED0000FF"),
    legendPosition = "none"
  )
  params_biplot <- list(data3,
    showLoadings = TRUE,
    lengthLoadingsArrowsFactor = 1.5,
    sizeLoadingsNames = 4,
    colLoadingsNames = "red4",
    # other parameters
    lab = NULL,
    hline = 0, vline = c(-25, 0, 25),
    vlineType = c("dotdash", "solid", "dashed"),
    gridlines.major = FALSE, gridlines.minor = FALSE,
    pointSize = 5,
    legendLabSize = 16, legendIconSize = 8.0,
    drawConnectors = FALSE,
    title = "PCA bi-plot",
    subtitle = "PC1 versus PC2",
    caption = "27 PCs ≈ 80%",
    returnPlot = TRUE,
    legendPosition = "bottom"
  )
  if (!is.null(biplotShapeBy) && biplotShapeBy != "") {
    params_biplot$shape <- biplotShapeBy
    params_pairsplot$shape <- biplotShapeBy
    t <- params_biplot[[1]]$metadata[,biplotShapeBy]
    params_biplot[[1]]$metadata[,biplotShapeBy] <- factor(t,
      levels = t[!duplicated(t)]
    )
    params_pairsplot[[1]]$metadata[,biplotShapeBy] <- factor(t,
      levels = t[!duplicated(t)]
    )
  }
  if (!is.null(biplotColBy) && biplotColBy != "") {
    params_pairsplot$colby <- biplotColBy
    params_pairsplot$colkey <- c("#00468BFF","#ED0000FF")
    params_biplot$colby <- biplotColBy
    params_biplot$colkey <- c("#00468BFF","#ED0000FF")
    t1 <- params_biplot[[1]]$metadata[,biplotColBy]
    params_biplot[[1]]$metadata[,biplotColBy] <- factor(t1,
      levels = t1[!duplicated(t1)]
    )
    params_pairsplot[[1]]$metadata[,biplotColBy] <- factor(t1,
      levels = t1[!duplicated(t1)]
    )
  }

  p2 <- do.call(PCAtools::pairsplot, params_pairsplot)
  p3 <- do.call(PCAtools::biplot, params_biplot)

  p4 <- PCAtools::plotloadings(
    data3,
    rangeRetain = 0.01, labSize = 4,
    components = getComponents(data3, c(1:plotloadingsComponents)),
    title = "Loadings plot", axisLabSize = 12,
    subtitle = "PC1, PC2, PC3, PC4, PC5",
    caption = "Top 1% variables",
    gridlines.major = FALSE, gridlines.minor = FALSE,
    shape = 24, shapeSizeRange = c(4, 8),
    col = c(plotloadingsLowCol, plotloadingsMidCol, plotloadingsHighCol),
    legendPosition = "none",
    drawConnectors = FALSE,
    returnPlot = TRUE
  )

  if (length(eigencorplotMetavars) > 0 && all(eigencorplotMetavars != "")) {
    metavars <- eigencorplotMetavars
  } else {
    metavars <- colnames(sampleInfo)[2:ncol(sampleInfo)]
  }
  if (length(metavars) == 1 && metavars != colnames(sampleInfo)[1]) {
    metavars <- c(colnames(sampleInfo)[1], metavars)
  } else if (length(metavars) == 1 && metavars == colnames(sampleInfo)[1]) {
    stop('eigencorplotMetavars need >= 2 feature')
  }

  p5 <- PCAtools::eigencorplot(
    data3,
    components = getComponents(data3, 1:eigencorplotComponents),
    metavars = metavars,
    cexCorval = 1.0,
    fontCorval = 2,
    posLab = "all",
    rotLabX = 45,
    scale = TRUE,
    main = "PC clinical correlates",
    cexMain = 1.5,
    plotRsquared = FALSE,
    corFUN = "pearson",
    corUSE = "na.or.complete",
    signifSymbols = c("****", "***", "**", "*", ""),
    signifCutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1),
    returnPlot = TRUE
  )

  p6 <- plot_grid(
    p1, p2, p3,
    ncol = 3,
    labels = c("A", "B  Pairs plot", "C"),
    label_fontfamily = "Arial",
    label_fontface = "bold",
    label_size = 22,
    align = "h",
    rel_widths = c(1.10, 0.80, 1.10)
  )

  p7 <- plot_grid(
    p4,
    as.grob(p5),
    ncol = 2,
    labels = c("D", "E"),
    label_fontfamily = "Arial",
    label_fontface = "bold",
    label_size = 22,
    align = "h",
    rel_widths = c(0.8, 1.2)
  )

  p <- plot_grid(
    p6, p7,
    ncol = 1,
    rel_heights = c(1.1, 0.9)
  )

  return(p)
}

## plot
p <- call_pcatools(
  datTable = data,
  sampleInfo = data2,
  biplotColBy = "ER",
  biplotShapeBy = "Grade",
  eigencorplotMetavars = colnames(data2)[-1],
  screeplotComponents = 30,
  pairsplotComponents = 3,
  plotloadingsComponents = 5,
  eigencorplotComponents = 10,
  top_var = 90,
  screeplotColBar = "#0085FF",
  plotloadingsLowCol = "#0085FF",
  plotloadingsMidCol = "#FFFFFF",
  plotloadingsHighCol = "#FF0000"
)

p
```


