---
title: "Perspective"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Perspective` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/perspective?lang=en>
:::

The three-dimensional perspective is a three-dimensional figure that can connect the higher values contained in a matrix with surfaces.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `shape`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("shape", quietly = TRUE)) {
  install.packages("shape")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(data.table)
library(jsonlite)
library(shape)
library(ggplotify)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data is a matrix.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/perspective/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data <- as.matrix(data)
col <- drapecol(data)

# View data
head(data[,1:5])
```

## Visualization

```{r fig-1perspective}
#| label: fig-1perspective
#| fig-cap: "Perspective"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 5
#| warning: false
#| error: false
#| message: false

# Perspective
p <- as.ggplot(function() {
  persp(as.matrix(data),
    theta = 45, phi = 20,
    expand = 0.5,
    r = 180, col = col,
    ltheta = 120,
    shade = 0.5,
    ticktype = "detailed",
    xlab = "X", ylab = "Y", zlab = "Z",
    border = "black" # could be NA
  )
  title("Perspective Plot", line = 0)
})

p
```

A clear view of a mountain peak.


