---
title: "Pyramid Stack"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Pyramid Stack` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/pyramid-stack?lang=en>
:::

The pyramid stack is a pyramid-like figure that distributes data on both sides of a central axis.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `ggthemes`; `dplyr`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("ggthemes", quietly = TRUE)) {
  install.packages("ggthemes")
}
if (!requireNamespace("dplyr", quietly = TRUE)) {
  install.packages("dplyr")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(ggthemes)
library(dplyr)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/pyramid-stack/data.json")$exampleData[[1]]$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data[,3] <- factor(data[,3], levels = unique(data[,3]))
data[,1] <- factor(data[,1], levels = unique(data[,1]))

# View data
head(data)
```

## Visualization

```{r fig-1pyramid-stack}
#| label: fig-1pyramid-stack
#| fig-cap: "Pyramid Stack"
#| out.width: "95%"
#| fig-height: 7
#| fig-width: 6
#| warning: false
#| error: false
#| message: false

# Pyramid Stack
p <- ggplot(data = data, aes(x = age, y = pop, fill = year)) +
  geom_bar(data = data %>% filter(gender == "female") %>% arrange(rev(year)),
           stat = "identity", position = "identity") +
  geom_bar(data = data %>% filter(gender == "male") %>% arrange(rev(year)),
           stat = "identity", position = "identity", mapping = aes(y = -pop)) +
  coord_flip() +
  geom_hline(yintercept = 0) +
  scale_fill_economist() +
  scale_fill_manual(values = c("#e04d39","#5bbad6","#1e9f86")) +
  labs(y = "pop | male (left) - female (right)", x= "") +
  theme_economist(horizontal = FALSE) +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "top",
        legend.direction = "horizontal",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

p
```



