---
title: "RCS-LRM"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `RCS-LRM` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/rcs-lrm?lang=en>
:::

Nonlinear regression analysis.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `rms`; `survival`; `ggplot2`; `stringr`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("rms", quietly = TRUE)) {
  install.packages("rms")
}
if (!requireNamespace("survival", quietly = TRUE)) {
  install.packages("survival")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("stringr", quietly = TRUE)) {
  install.packages("stringr")
}

# Load packages
library(data.table)
library(jsonlite)
library(rms)
library(survival)
library(ggplot2)
library(stringr)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/rcs-lrm/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data <- na.omit(data)
ex <- set::not(colnames(data), c("main", "group"))
ex <- str_c(ex, collapse = "+")
dd <<- datadist(data)
options(datadist = "dd")
for (i in 3:5) {
  fit <- lrm(as.formula(paste0("group~rcs(main,nk=i,inclx = T)+", ex, collapse = "+")), data = data, x = TRUE)
  tmp <- AIC(fit)
  if (i == 3) {
    AIC <- tmp
    nk <<- 3
  }
  if (tmp < AIC) {
    AIC <- tmp
    nk <<- i
  }
}
fit <- lrm(as.formula(paste0("group~rcs(main,nk=nk,inclx = T)+", ex, collapse = "+")), data = data, x = TRUE)
dd$limits$main[2] <- median(data$main)
fit <- update(fit)
orr <- Predict(fit, main, fun = exp, ref.zero = TRUE)

# View data
head(data)
```

## Visualization

```{r fig-1rcs-lrm}
#| label: fig-1rcs-lrm
#| fig-cap: "RCS-LRM"
#| out.width: "95%"
#| fig-height: 2.5
#| fig-width: 4
#| warning: false
#| error: false
#| message: false

# RCS-LRM
p <- ggplot() +
  geom_line(data = orr, aes(main, yhat), linetype = "solid", size = 1, alpha = 1,
            colour = "#FF0000") +
  geom_ribbon(data = orr, aes(main, ymin = lower, ymax = upper), alpha = 0.6, 
              fill = "#FFC0CB") +
  geom_hline(yintercept = 1, linetype = 2, size = 0.5) +
  geom_vline(xintercept = dd$limits$main[2], linetype = 2, size = 0.5) +
  labs(x = "main", y = "Odds Ratio(95%CI)") +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))
 
p
```



