---
title: "Rose Chart"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Rose Chart` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/rose-chart?lang=en>
:::

The rose chart is a column chart drawn in polar coordinates. The radius of the arc is used to indicate the size of the data.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data is divided into three columns, the first column is the sample name, the second column is the grouping, and the third column is the value corresponding to the sample.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/rose-chart/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
data[, 2] <- factor(data[, 2], levels = unique(data[, 2]))

# View data
head(data)
```

## Visualization

```{r fig-1rose-chart}
#| label: fig-1rose-chart
#| fig-cap: "Rose Chart"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 6
#| warning: false
#| error: false
#| message: false

# Rose Chart
p <- ggplot(data, aes(x = Sample, y = Freq)) +
  geom_col(aes(fill = Group), width = 0.9, size = 0, alpha = 0.8) +
  coord_polar() +
  ggtitle("Rose Chart") +
  scale_fill_manual(values = c("#E64B35FF", "#4DBBD5FF")) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5))

p
```

The case data is the distribution of up- and down-regulated genes in different organs after using scRNA-Seq to sequence different human organs.



