---
title: "Sankey"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Sankey` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/sankey?lang=en>
:::

Sankey diagrams are a type of flow diagramin which the width of the arrows is proportional to the flow rate.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggalluvial`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggalluvial", quietly = TRUE)) {
  install.packages("ggalluvial")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggalluvial)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data are the four variables and the frequency of combination of four variables.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/sankey/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
value <- "Freq"
axis <- c("Class", "Sex")
usr_axis <- c()
for (i in seq_len(length(axis))) {
  usr_axis <- c(usr_axis, axis[i])
  assign(paste0("axis", i), axis[i])
}
index_axis <- match(usr_axis, colnames(data))
index_value <- match(value, colnames(data))
data1 <- data[, c(index_value, index_axis)]
## define band color
nlevels <- as.numeric(apply(data1[, -1], 2, function(data) {
  return(length(unique(data)))
}))
band_color <- c("#8DD3C7", "#FFFFB3", "#BEBADA", "#FB8072", "#8DD3C7", "#FFFFB3")
## rename data
data_rename <- data1
colnames(data_rename) <- c(
  "value",
  paste("axis", seq_len(length(usr_axis)), sep = "")
)

# View data
head(data)
```

## Visualization

```{r fig-1sankey}
#| label: fig-1sankey
#| fig-cap: "Sankey"
#| out.width: "95%"
#| fig-height: 2.5
#| fig-width: 4
#| warning: false
#| error: false
#| message: false

# Sankey
p <- ggplot(data_rename, aes(y = value, axis1 = axis1, axis2 = axis2)) +
  geom_alluvium(alpha = 1, aes(fill = data1[, colnames(data1) == "Sex"]),
                width = 0, reverse = FALSE) +
  scale_x_discrete(limits = usr_axis, expand = c(0.02, 0.1)) +
  ylab("") +
  scale_fill_discrete(name = "Sex") +
  coord_flip() +
  geom_stratum(alpha = 1, width = 1 / 8, reverse = FALSE, fill = band_color,
               color = "white") +
  geom_text(stat = "stratum", infer.label = TRUE, reverse = FALSE) +
  ggtitle("Sankey plot") +
  guides(fill = guide_legend(title = "Sex")) +
  scale_fill_manual(values = c("#00468BFF", "#ED0000FF")) +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

The color of female shunting is blue, the color of male shunting is red, and the width of blue shunting is equal to the total width of female.



