---
title: "3D-Scatter"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `3D-Scatter` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/scatter-3d?lang=en>
:::

3D scatter plot is to apply a number of quantitative variables to different coaxes in space and combine different variables into coordinates in space, so as to clearly explain the interaction between the three quantitative variables.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `plot3D`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("plot3D", quietly = TRUE)) {
  install.packages("plot3D")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(data.table)
library(jsonlite)
library(plot3D)
library(ggplotify)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data are three variables and grouping.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/scatter-3d/data.json")$exampleData[[1]]$textarea[[1]])
data <- as.data.frame(data)

# Convert data structure
col_idx <- which(colnames(data) == "group")
data[, col_idx] <- as.factor(data[, col_idx])
shapes <- 19
shape_idx <- ""

# View data
head(data)
```

## Visualization

```{r fig-1scatter-3d}
#| label: fig-1scatter-3d
#| fig-cap: "3D-Scatter"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# 3D-Scatter
p <- as.ggplot(function() {
  plot3d <- scatter3D(data[, 1], data[, 2], data[, 3],
    pch = shapes, cex = 1,
    phi = 0, theta = 45, ticktype = "detailed",
    bty = "b2", colkey = FALSE, alpha = 1,
    xlab = colnames(data)[1], ylab = colnames(data)[2],
    zlab = colnames(data)[3],
    main = "3D-Scatter Plot",
    colvar = as.numeric(as.factor(data[, 4])),
    col = c("#e04d39","#5bbad6","#1e9f86")
  )
  
  legend("right", pch=19, legend = levels(data[, col_idx]),
         cex = 1.1, bty = 'n', xjust = 0.5, horiz = F,
         title = colnames(data)[col_idx],
         col = c("#e04d39","#5bbad6","#1e9f86"))
})

p
```

In the figure, temperature, pressure and time are respectively placed on x (horizontal axis), Y (vertical axis) and Z (perspective axis) to generate a THREE-DIMENSIONAL scatter plot, and the correlation between variables and their correlation degree can be intuitively found.



