---
title: "Scatterpie"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Scatterpie` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/scatterpie?lang=en>
:::

Scatter Pie can be used to visualize data fraction in different space coordinates.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `scatterpie`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("scatterpie", quietly = TRUE)) {
  install.packages("scatterpie")
}

# Load packages
library(data.table)
library(jsonlite)
library(scatterpie)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/scatterpie/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1scatterpie}
#| label: fig-1scatterpie
#| fig-cap: "Scatterpie"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 7
#| warning: false
#| error: false
#| message: false

# Scatterpie
p <- ggplot() +
  geom_scatterpie(data = data, aes(x = x, y = y), cols = colnames(data)[-c(1, 2)]) +
  scale_fill_manual(values = c("#E64B35FF","#4DBBD5FF","#00A087FF","#3C5488FF")) +
  labs(x="x", y="y") +
  theme_minimal() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```




