---
title: "Simple Funnel Diagram"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Simple Funnel Diagram` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/simple-funnel-diagram?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `magrittr`; `echarts4r`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("magrittr", quietly = TRUE)) {
  install.packages("magrittr")
}
if (!requireNamespace("echarts4r", quietly = TRUE)) {
  install.packages("echarts4r")
}

# Load packages
library(data.table)
library(jsonlite)
library(magrittr)
library(echarts4r)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/simple-funnel-diagram/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1simple-funnel-diagram}
#| label: fig-1simple-funnel-diagram
#| fig-cap: "Simple Funnel Diagram"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 6
#| warning: false
#| error: false
#| message: false

# Simple Funnel Diagram
p <- data %>%
  e_charts() %>%
  e_funnel(value, key) %>%
  e_title("Funnel") %>%
  e_theme("macarons")

p
```



