---
title: "Slopegraph"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Slopegraph` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/slopegraph?lang=en>
:::

Sopegraph can be used to display the change of values.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `CGPfunctions`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("CGPfunctions", quietly = TRUE)) {
  install.packages("CGPfunctions")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(CGPfunctions)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/slopegraph/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data[, "country"] <- factor(data[ ,"country"], levels = unique(data[ ,"country"]))
data[, "year"] <- factor(data[ ,"year"], levels = unique(data[ ,"year"]))

# View data
head(data)
```

## Visualization

```{r fig-1slopegraph}
#| label: fig-1slopegraph
#| fig-cap: "Slopegraph"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 7
#| warning: false
#| error: false
#| message: false

# Slopegraph
p <- newggslopegraph(data, year, lifeExp, country) +
  labs(subtitle = "", title = "Slope Graph", x = "Life Expectancy (years)",
       y = "country", caption = "") +
  scale_color_manual(values = c("#3B4992FF", "#EE0000FF", "#008B45FF",
                               "#631879FF", "#008280FF", "#BB0021FF")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

p
```



