---
title: "Percentsge Stacked Bar Chart"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Percentsge Stacked Bar Chart` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/stacked-percentage-bar-chart?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`; `dplyr`; `tidyr`; `scales`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("dplyr", quietly = TRUE)) {
  install.packages("dplyr")
}
if (!requireNamespace("tidyr", quietly = TRUE)) {
  install.packages("tidyr")
}
if (!requireNamespace("scales", quietly = TRUE)) {
  install.packages("scales")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The case data represents the sales percentage of three different products in a shopping mall over the course of one week.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/stacked-percentage-bar-chart/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data$total <- rowSums(data[, -1])
data_long <- gather(data, kinds, value, -days, -total)
data_long <- data_long %>%
  group_by(days) %>%
  mutate(percent = value / total * 100)
data_long[["days"]] <- factor(data_long[["days"]], levels = data[["days"]])

# View data
head(data)
```

## Visualization

```{r fig-1stacked-percentage-bar-chart}
#| label: fig-1stacked-percentage-bar-chart
#| fig-cap: "Percentsge Stacked Bar Chart"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# Percentsge Stacked Bar Chart
p <- ggplot(data_long, aes(x = percent, y = days, fill = kinds)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = ifelse(percent != 0, paste0(round(percent), "%"), "")),
            position = position_stack(vjust = 0.5)) +
  labs(title = "Percentage Stacked Bar Chart", x = "Percentage", y = "Days") +
  scale_x_continuous(labels = percent_format(scale = 1)) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(values = c("#E64B35FF","#4DBBD5FF","#00A087FF"))

p
```



