---
title: "Time ROC"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Time ROC` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/time-roc?lang=en>
:::

Receiver Operating Characteristic (ROC) analysis with time records in survival analysis.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `plotROC`; `survivalROC`; `ggplot2`; `grid`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("plotROC", quietly = TRUE)) {
  install.packages("plotROC")
}
if (!requireNamespace("survivalROC", quietly = TRUE)) {
  install.packages("survivalROC")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("grid", quietly = TRUE)) {
  install.packages("grid")
}

# Load packages
library(data.table)
library(jsonlite)
library(plotROC)
library(survivalROC)
library(ggplot2)
library(grid)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

- <Table1>: (Numeric) survival data (i.e survive, risk).
- <Table2>: (Numeric) time data.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data1 <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/time-roc/data.json")$exampleData$textarea[[1]])
data1 <- as.data.frame(data1)
data2 <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/time-roc/data.json")$exampleData$textarea[[2]])
data2 <- as.data.frame(data2)

# convert data structure
surv_table <- data1
colnames(surv_table) <- c("surv", "cens", "risk")
mtime <- as.data.frame(data2)[, 1]
sroc <- lapply(mtime, function(t) {
  stroc <- survivalROC(
    Stime = surv_table$surv,
    status = surv_table$cens,
    marker = surv_table$risk,
    predict.time = t,
    method = "KM"
  )
  data.frame(
    TPF = stroc[["TP"]],
    FPF = stroc[["FP"]],
    cut = stroc[["cut.values"]],
    time = rep(
      stroc[["predict.time"]],
      length(stroc[["TP"]])
    ),
    AUC = rep(
      stroc$AUC,
      length(stroc$FP)
    )
  )
})
mroc <- do.call(rbind, sroc)
mroc$time <- factor(mroc$time)

# View data
head(data1)
head(data2)
```

## Visualization

```{r fig-1time-roc}
#| label: fig-1time-roc
#| fig-cap: "Time ROC"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 7
#| warning: false
#| error: false
#| message: false

# Time ROC
col <- c("#E64B35FF","#4DBBD5FF","#00A087FF","#3C5488FF","#F39B7FFF")
p <- ggplot(mroc, aes(x = FPF, y = TPF, label = cut, color = time)) +
  plotROC::geom_roc(labels = FALSE, stat = "identity", n.cuts = 0) +
  geom_abline(slope = 1, intercept = 0, color = "red", linetype = 2) +
  labs(title = "ROC Dependence Time", x = "False positive rate",
       y = "True positive rate", 
       color = paste("Time", "(", "Year", ")")) +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12, hjust = 0.5),
        axis.title = element_text(size = 10),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) +
  scale_color_manual(values = col)

auc <- levels(factor(mroc$AUC))
for (i in 1:length(auc)) {
  p <- p + annotate("text",
    x = 0.75,
    y = 0.05 + 0.05 * i, ## 注释text的位置
    col = col[i],
    label = paste(
      paste(paste(mtime[i], "Year", sep = " "), " = "),
      round(as.numeric(auc[i]), 2)
    )
  )
}

p
```



