---
title: "Treeheatr"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Treeheatr` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/treeheatr?lang=en>
:::

The heatmap decision tree is a visualization graph that combines two types of graphs: heatmap and decision tree visualization.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `treeheatr`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("treeheatr", quietly = TRUE)) {
  install.packages("treeheatr")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(data.table)
library(jsonlite)
library(treeheatr)
library(ggplotify)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The first column is the name of the species, the second column is the island, and the rest are the species characteristics.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/treeheatr/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
x <- data
wrong_cols <- suppressWarnings(sapply(x, function(x) {
  if (!is.numeric(x)) {
    sum(!is.na(as.numeric(x))) > 0.7 * length(x)
  } else {
    FALSE
  }
}))
if (any(wrong_cols)) {
  ix <- which(wrong_cols)
  for (i in ix) {
    data[[i]] <- suppressWarnings(as.numeric(data[[i]]))
  }
  rm(ix)
}
rm(x, wrong_cols)

# View data
head(data)
```

## Visualization

```{r fig-1treeheatr}
#| label: fig-1treeheatr
#| fig-cap: "Treeheatr"
#| out.width: "95%"
#| fig-height: 3
#| fig-width: 6
#| warning: false
#| error: false
#| message: false

# Treeheatr
p <- as.ggplot(function() {
  print(heat_tree(data,
    target_lab = "species",
    task = 'classification',
    show = "heat-tree",
    heat_rel_height = 0.2,
    panel_space = 0.001,
    clust_samps = T,
    clust_target = T,
    lev_fac = 1.3,
    cont_legend = F,
    cate_legend = F
  ))
})

p
```

The upper half of the figure is a decision diagram, and the lower half is a heat map.

Decision tree: The topmost island has the greatest influence on the classification of species, and can be classified into different species according to different conditions.

Heatmap: you can observe the changes in the amount of each species under each condition.

Legend: For each categorical variable, different colors indicate different types; for continuous variables, the higher the value, the lighter the color, otherwise, the darker.


