---
title: "Tricolor Histogram"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Tricolor Histogram` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/tricolor-histogram?lang=en>
:::

The tricolored histogram divides the histogram into three regions: low-value zone, middle-value zone, and high-value zone, using three different colors.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/tricolor-histogram/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data$draw_color <- ifelse(data$value < 5, "#F44336",
                          ifelse(data$value > 7, "#006064", "#3F51B5")
)

# View data
head(data)
```

## Visualization

```{r fig-1tricolor-histogram}
#| label: fig-1tricolor-histogram
#| fig-cap: "Tricolor Histogram"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# Tricolor Histogram
p <- ggplot(data, aes(x = values, fill = draw_color)) +
  geom_histogram(alpha = 0.5, binwidth = 0.05, position = "identity") +
    scale_fill_manual(values = c("#3F51B5", "#006064", "#F44336")) +
  theme_bw()

p
```


