---
title: "UMAP"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `UMAP` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/umap?lang=en>
:::

UMAP is a nonlinear dimensionality reduction algorithm suitable for high-dimensional data reduction to two or three dimensions and visualization. The algorithm can make the t distribution of points with greater similarity closer in the lower dimensional space. For low similarity points, the t distribution is farther away in the low dimensional space.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `umap`; `ggpubr`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("umap", quietly = TRUE)) {
  install.packages("umap")
}
if (!requireNamespace("ggpubr", quietly = TRUE)) {
  install.packages("ggpubr")
}

# Load packages
library(data.table)
library(jsonlite)
library(umap)
library(ggpubr)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data are the data set (gene name and corresponding gene expression value) and sample information (sample name and grouping).

```{r load data, message=FALSE, warning=FALSE}
# Load data
data1 <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/umap/data.json")$exampleData$textarea[[1]])
data1 <- as.data.frame(data1)
data2 <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/umap/data.json")$exampleData$textarea[[2]])
data2 <- as.data.frame(data2)

# convert data structure
sample.info <- data2
rownames(data1) <- data1[, 1]
data1 <- as.matrix(data1[, -1])
## umap
set.seed(123)
umap_info <- umap(t(data1))
colnames(umap_info$layout) <- c("UMAP_1", "UMAP_2")
# handle data
umap_data <- data.frame(
  sample = colnames(data1),
  umap_info$layout
)
colorBy <- sample.info[match(colnames(data1), sample.info[, 1]), "Species"]
colorBy <- factor(colorBy, level = colorBy[!duplicated(colorBy)])
umap_data$colorBy = colorBy
shapeBy <- NULL

# View data
head(data1[,1:5])
head(data2)
```

## Visualization

```{r fig-1umap}
#| label: fig-1umap
#| fig-cap: "umap"
#| out.width: "95%"
#| fig-height: 3
#| fig-width: 4
#| warning: false
#| error: false
#| message: false

# umap
p <- ggscatter(data = umap_data, x = "UMAP_1", y = "UMAP_2", size = 2, 
               palette = "lancet", color = "colorBy") +
  labs(color = "group") +
  ggtitle("UMAP Plot") +
  theme_classic() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

Different colors represent different samples, which is the same as PCA (principal component analysis) graphic interpretation. The difference lies in the visualization effect. For dissimilar points in T-SNE, a small distance will generate a large gradient to repel them.


