---
title: "Upset Plot"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Upset Plot` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/upset-plot?lang=en>
:::

Upset can be used to show the interactive relationship between collections.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `VennDiagram`; `ComplexHeatmap`; `ggplotify`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("VennDiagram", quietly = TRUE)) {
  install.packages("VennDiagram")
}
if (!requireNamespace("ComplexHeatmap", quietly = TRUE)) {
  BiocManager::install("ComplexHeatmap")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(VennDiagram)
library(ComplexHeatmap)
library(ggplotify)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

There are two types of data tables: list and binary. The list format is that each column is a set and contains all the elements corresponding to the set. In the binary format, the first column is all the elements of all sets, and the subsequent columns are a numeric matrix composed of 0 and 1. 1 indicates that the corresponding row element exists in a certain set, and 0 indicates that it does not exist.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/upset-plot/data.json")$exampleData[[1]]$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
for (i in seq_len(ncol(data))) {
  data[is.na(data[, i]), i] <- ""
}
data2 <- as.list(data)
data2 <- lapply(data2, function(x) {x[x != ""]})
data2 <- list_to_matrix(data2)
m = make_comb_mat(data2, mode = "distinct")
ss = set_size(m)
cs = comb_size(m)
set_order <- order(ss)
comb_order <- order(comb_degree(m), -cs)

# View data
head(data)
```

## Visualization

```{r fig-1upset-plot}
#| label: fig-1upset-plot
#| fig-cap: "Upset Plot"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 10
#| warning: false
#| error: false
#| message: false

# Upset Plot
p <- as.ggplot(function(){
  top_annotation <- HeatmapAnnotation(
    Intersections = anno_barplot(
      cs, ylim = c(0, max(cs)*1.1), 
      border = FALSE, 
      gp = gpar(fill = "#000000", fontsize = 10), 
      height = unit(5, "cm")
    ), 
    annotation_name_side = "left", 
    annotation_name_rot = 90
  )
  
  left_annotation <- rowAnnotation(
    Numbers = anno_barplot(-ss, axis_param = list(
      at = seq(-max(ss), 0, round(max(ss)/5)),
      labels = rev(seq(0, max(ss), round(max(ss)/5))),
      labels_rot = 0),
      baseline = 0,
      border = FALSE, 
      gp = gpar(fill = "#000000", fontsize = 10), 
      width = unit(4, "cm")
    ),
    set_name = anno_text(set_name(m), location = 0.5,  just = "center",
                         width = max_text_width(set_name(m)) + unit(5, "mm"))
  )
  
  ht = UpSet(m, comb_col = "#000000", bg_col = "#F0F0F0", bg_pt_col = "#CCCCCC",
             pt_size = unit(3, "mm"), lwd = 2, set_order = set_order,
             comb_order = comb_order, top_annotation = top_annotation,
             left_annotation = left_annotation,  right_annotation = NULL,
             show_row_names = FALSE)
  ht = draw(ht)
  od = column_order(ht)
  decorate_annotation("Intersections", {
    grid.text(cs[od], x = seq_along(cs), y = unit(cs[od], "native") + unit(2, "pt"),
              default.units = "native", just = c("left", "bottom"), 
              gp = gpar(fontsize = 10, col = "#000000",
              fontfamily = "Arial"), hjust = 0.5)
  })
})
p <- p + ggtitle("Upset Plot") + 
  theme(plot.title = element_text(hjust = 0.6))

p
```



