---
title: "Venn"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Venn` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/venn?lang=en>
:::

A Venn diagram is a diagramthat shows all possible logical relations between a finite collection of different sets. These diagrams depict elements as points in the plane, and sets as regions inside closed curves. A Venn diagram consists of multiple overlapping closed curves, usually circles, each representing a set. The points inside a curve labelled S represent elements of the set S, while points outside the boundary represent elements not in the set S. This lends to easily read visualizations; for example, the set of all elements that are members of both sets Sand T, S ∩ T, is represented visually by the area of overlap of the regions S and T. In Venn diagrams the curves are overlapped in every possible way, showing all possible relations between the sets.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `VennDiagram`; `grDevices`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("VennDiagram", quietly = TRUE)) {
  install.packages("VennDiagram")
}
if (!requireNamespace("grDevices", quietly = TRUE)) {
  install.packages("grDevices")
}

# Load packages
library(data.table)
library(jsonlite)
library(VennDiagram)
library(grDevices)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data is a collection of five gene names.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/venn/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
for (i in seq_len(ncol(data))) {
  data[is.na(data[, i]), i] <- ""
}
raw <- data
data <- as.data.frame(raw[raw[, 1] != "", 1])
colnames(data) <- colnames(raw)[1]
list.num <- 1
for (i in 2:ncol(raw)) {
  if (any(!is.na(raw[, i]) & raw[, i] != "")) {
    tmp <- raw[i]
    tmp <- tmp[tmp[, 1] != "", ]
    tmp <- as.data.frame(tmp)
    colnames(tmp) <- colnames(raw)[i]
    assign(paste0("data", i), tmp)
    list.num <- list.num + 1
  }
}
colnames(data) <- paste("V", seq_len(ncol(data)), sep = "")
colnames(data2) <- paste("V", seq_len(ncol(data2)), sep = "")
colnames(data3) <- paste("V", seq_len(ncol(data3)), sep = "")
colnames(data4) <- paste("V", seq_len(ncol(data4)), sep = "")
colnames(data5) <- paste("V", seq_len(ncol(data5)), sep = "")
data_list <- list(
  n1 = data$V1, n2 = data2$V1, n3 = data3$V1,
  n4 = data4$V1, n5 = data5$V1
)
names(data_list) <- colnames(raw)[1:5]

# View data
head(data)
```

## Visualization

```{r fig-1venn}
#| label: fig-1venn
#| fig-cap: "Venn"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 5
#| warning: false
#| error: false
#| message: false

# Venn
col <- c("#E64B35FF","#4DBBD5FF","#00A087FF","#3C5488FF","#F39B7FFF")
p <- venn.diagram(
  data_list, scaled = F, euler.d = F, filename = NULL, col = "black",
  fill = col,
  cex = c(
    1.5, 1.5, 1.5, 1.5, 1.5, 1, 0.8, 1, 0.8, 1, 0.8, 1, 0.8,
    1, 0.8, 1, 0.55, 1, 0.55, 1, 0.55, 1, 0.55, 1, 0.55, 1, 1, 1, 1, 1, 1.5
  ),
  cat.col = col, cat.cex = 1,
  main.fontfamily = "Arial", fontfamily = "Arial", cat.fontface = "bold",
  cat.fontfamily = "Arial", margin = 0.1, main = "Vene Plot", alpha = 0.8
);grid::grid.draw(p)
```

The closed curve of 5 colors represents 5 sets, and the number represents the number of overlapping or non-overlapping genes in multiple sets. For example, 8 in the sample figure represents 8 identical gene names in 5 sample sets.


