---
title: "Venn2"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Venn2` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/venn2?lang=en>
:::

A Venn diagram is a diagramthat shows all possible logical relations between a finite collection of different sets. These diagrams depict elements as points in the plane, and sets as regions inside closed curves. A Venn diagram consists of multiple overlapping closed curves, usually circles, each representing a set. The points inside a curve labelled S represent elements of the set S, while points outside the boundary represent elements not in the set S. This lends to easily read visualizations; for example, the set of all elements that are members of both sets Sand T, S ∩ T, is represented visually by the area of overlap of the regions S and T. In Venn diagrams the curves are overlapped in every possible way, showing all possible relations between the sets.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `venn`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("venn", quietly = TRUE)) {
  install.packages("venn")
}

# Load packages
library(data.table)
library(jsonlite)
library(venn)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data is a collection of five gene names.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/venn2/data.json")$exampleData[[1]]$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data_venn <- as.list(data)
data_venn <- lapply(data_venn, function(x) {
  x[is.na(x)] <- ""
  x <- x[x != ""]
  return(x)
})

# View data
head(data)
```

## Visualization

```{r fig-1venn2}
#| label: fig-1venn2
#| fig-cap: "Venn2"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 5
#| warning: false
#| error: false
#| message: false

# Venn2
col <- c("#E64B35FF","#4DBBD5FF","#00A087FF","#3C5488FF","#F39B7FFF")
venn(x=data_venn, opacity=0.8, ggplot=F, ilabels = TRUE, zcolor=col, box=F)
title(main = "Vene Plot (5 sets)", line = -1)
```

The closed curve of 5 colors represents 5 sets, and the number represents the number of overlapping or non-overlapping genes in multiple sets. For example, 8 in the sample figure represents 8 identical gene names in 5 sample sets.


