---
title: "Volcano"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Volcano` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/volcano?lang=en>
:::

The volcanogram is a visual representation of the difference in gene expression between two samples.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `ggpubr`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("ggpubr", quietly = TRUE)) {
  install.packages("ggpubr")
}

# Load packages
library(data.table)
library(jsonlite)
library(ggpubr)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data is the gene name and its corresponding logFC and p.value.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/volcano/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
## Perform log10 transformation on the difference p (adj.P.Val column)
data[, "logP"] <- -log10(as.numeric(data[, "P.Value"]))
data[, "logFC"] <- as.numeric(data[, "logFC"])
## Add a new column Group
data[, "Group"] <- "not-significant"
## Up and down
data$Group[which((data[, "P.Value"] < 0.05) & (data$logFC >= 2))] <- "Up-regulated"
data$Group[which((data[, "P.Value"] < 0.05) & (data$logFC <= 2 * -1))] <- "Down-regulated"
## Add a new column Label
data[["Label"]] <- ""
## Sort the p-values of differentially expressed genes from small to large
data <- data[order(data[, "P.Value"]), ]
## Among the highly expressed genes, select the 10 with the smallest adj.P.Val
up_genes <- head(data[, "Symbol"][which(data$Group == "Up-regulated")], 10)
down_genes <- head(data[, "Symbol"][which(data$Group == "Down-regulated")], 10)
not_sig_genes <- NA
## Merge up_genes and down_genes and add them to Label
deg_top_genes <- c(as.character(up_genes), as.character(not_sig_genes),
as.character(down_genes))
deg_top_genes <- deg_top_genes[!is.na(deg_top_genes)]
data$Label[match(deg_top_genes, data[, "Symbol"])] <- deg_top_genes

# View data
head(data)
```

## Visualization

```{r fig-1volcano}
#| label: fig-1volcano
#| fig-cap: "Volcano"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 6
#| warning: false
#| error: false
#| message: false

# Volcano
options(ggrepel.max.overlaps = 100)
p <- ggscatter(data, x = "logFC", y = "logP", color = "Group", 
               palette = c("#2f5688", "#BBBBBB", "#CC0000"), size = 1, 
               alpha = 0.5, font.label = 8, repel = TRUE, label=data$Label,
               xlab = "log2(Fold Change)", ylab = "-log10(P Value)",
               show.legend.text = FALSE) +
  ggtitle("Volcano Plot") +
  geom_hline(yintercept = -log(0.05, 10), linetype = "dashed") +
  geom_vline(xintercept = c(2, -2), linetype = "dashed") +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

The horizontal axis is denoted by log2 (fold change), and the more different genes are distributed at both ends of the picture.The ordinate is denoted by -log10 (p.value) and is the negative log of the P value of T test significance.Blue dots represent down-regulated genes, red dots represent up-regulated genes, and gray dots represent genes that are not significantly different.


