---
title: "Waffle Plot"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Waffle Plot` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/waffle?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `waffle`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("waffle", quietly = TRUE)) {
  remotes::install_github("hrbrmstr/waffle")
}

# Load packages
library(data.table)
library(jsonlite)
library(waffle)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/waffle/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
parts <- data[,2]

# View data
head(data)
```

## Visualization

```{r fig-1waffle}
#| label: fig-1waffle
#| fig-cap: "Waffle Plot"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 10
#| warning: false
#| error: false
#| message: false

# Waffle Plot
p <- waffle(parts, rows = 8, size = 1, legend_pos = "right") +
  ggtitle("Waffle Plot") +
  scale_fill_manual(values = c("#e04d39","#5bbad6","#1e9f86")) +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```



