---
title: "Waterfalls Plot2"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Waterfalls Plot2` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/waterfalls-plot?lang=en>
:::

Used to visualize changes in data, with the difference from version 1 being the ability to customize the colors for upward and downward values.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `waterfalls`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("waterfalls", quietly = TRUE)) {
  install.packages("waterfalls")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(waterfalls)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/waterfalls-plot/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# convert data structure
data[["name"]] <- factor(data[["name"]], levels = data[["name"]])
data$fill <- ifelse(data$value > 0, "#B71C1C", "#1B5E20")

# View data
head(data)
```

## Visualization

```{r fig-1waterfalls-plot}
#| label: fig-1waterfalls-plot
#| fig-cap: "Waterfalls Plot2"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# Waterfalls Plot2
p <- waterfall(data, calc_total = T, rect_width = 0.7, fill_by_sign = F,
               fill_colours = data$fill, total_rect_color = "#1E065D") +
  theme_bw()

p
```



