---
title: "Waterfalls"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Waterfalls` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/waterfalls?lang=en>
:::

The waterfall chart is used to display the cumulative effect of sequentially introduced positive or negative values . These intermediate values can either be time based or category based.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `data.table`; `jsonlite`; `waterfalls`; `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("data.table", quietly = TRUE)) {
  install.packages("data.table")
}
if (!requireNamespace("jsonlite", quietly = TRUE)) {
  install.packages("jsonlite")
}
if (!requireNamespace("waterfalls", quietly = TRUE)) {
  install.packages("waterfalls")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(data.table)
library(jsonlite)
library(waterfalls)
library(ggplot2)
```

```{r}
sessioninfo::session_info("attached")
```

## Data Preparation

The loaded data have two columns, with the first for category based items and the second for their corresponding values.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- data.table::fread(jsonlite::read_json("https://hiplot.cn/ui/basic/waterfalls/data.json")$exampleData$textarea[[1]])
data <- as.data.frame(data)

# View data
head(data)
```

## Visualization

```{r fig-1waterfalls}
#| label: fig-1waterfalls
#| fig-cap: "Waterfalls"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# Waterfalls
p <- waterfall(data, rect_text_labels = data$value, rect_text_size = 1,
    rect_text_labels_anchor = "centre", calc_total = T,
    total_axis_text = "Total", total_rect_text = sum(data$value),
    total_rect_color = "steelblue", total_rect_text_color = "black",
    rect_width = 0.7, rect_border = "black", draw_lines = TRUE,
    linetype = 2, fill_by_sign = F, 
    fill_colours = c("#E64B35FF","#4DBBD5FF","#00A087FF","#3C5488FF","#F39B7FFF",
                     "#8491B4FF"),
    scale_y_to_waterfall = T) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5)) +
  labs(title = "Waterfalls Plot")

p
```

As shown in the example figure, the x-axis represent each category based items, the y-axis showing their cumulative values. Increments and decrements that are sufficiently extreme can cause the cumulative total to fall above and below the axis at various points.


